
\section{\sc Peer-Reviewed Journal Publications}

Asterick by my name denote that I am the corresponding author (leading research) when not in first author position.

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

% The comment layer -- a private record that travels with the source but never
% renders in the PDF. Track each paper's lifecycle with the greppable @pub tag
% (every example here is fictional):
%   @pub submitted=2023-01-15 r1=2023-04-02(major) resubmitted=2023-05-20 accepted=2023-07-01 online=2023-07-18
% Later, `grep '@pub' src/*.tex` turns these into a dataset -- e.g. how long each journal really takes.
\item
Messina, J., Luo, R., Xu, K., Lu, G., Deng, H., \textbf{Tschopp, M.A.}, Gao, F., ``\href{https://doi.org/10.1016/j.scriptamat.2021.114150}{Machine learning to predict aluminum segregation to magnesium grain boundaries},'' Scripta Materialia, 204 (2021) 114150.

\item
Paudel, Y., Giri, D., Priddy, M.W., Barrett, C.D., Inal, K.,  \textbf{Tschopp, M.A.}, Rhee, H., El Kadiri, H., ``\href{https://doi.org/10.3390/met11091373}{A Review on Capturing Twin Nucleation in Crystal Plasticity for Hexagonal Metals},'' Metals, 11(9) (2021) 1373:1-53.

\item
Dyar, C., Brauer, S., Williams, W., Doude, H., Whittington, W., Oppedal, A., El Kadiri, H., \textbf{Tschopp, M.A.}, Rhee, H., ``\href{https://doi.org/10.1007/s11665-020-05005-3}{Enhancing Mechanical Properties of Hot Wrought Steel by Microalloying and Optimizing Heat Treatments},'' Journal of Materials Engineering and Performance, 29(8) (2020) 5374--5387.

\item
Chavoshi, S.Z., \textbf{Tschopp, M.A.}, Branicio, P.S., ``\href{https://doi.org/10.1080/14786435.2019.1637033}{Transition of deformation mechanisms in nanotwinned single crystalline SiC},'' Philosophical Magazine 99(21) (2019) 2636--2660.

\item
{Khanzadeh, M.}, {Chowdhury, S.}, \textbf{Tschopp, M.A.}, Doude, H., Marufuzzaman, M., Bian, L., ``\href{https://doi.org/10.1080/24725854.2017.1417656}{In-situ monitoring of melt pool images for porosity prediction in directed energy deposition processes},'' Institute of Industrial and Systems Engineers (IISE) Transactions, 51(5) (2019) 437--455.
\begin{list2}
\item[$\star$] ``\href{https://www.iise.org/iemagazine/2019-04/html/research/research.html}{Enabling `lab-to-fab' transition of metal-based additive manufacturing}'' was highlighted by IISE Transactions
\end{list2}

\item
{Aboutaleb, A.M.}, Mahtabi, M.J., \textbf{Tschopp, M.A.}, Bian, L., ``\href{https://doi.org/10.1016/j.jmapro.2018.12.040}{Multi-objective accelerated process optimization of mechanical properties in laser-based additive manufacturing: Case study on Selective Laser Melting (SLM) Ti-6Al-4V},'' Journal of Manufacturing Processes, 38 (2019) 432--444.

\item
Seifi, S.H., Tian, W., Doude, H., \textbf{Tschopp, M.A.}, Bian, L.,  ``\href{https://doi.org/10.1115/1.4043898}{Layer-wise modeling and anomaly detection for laser-based additive manufacturing},'' Journal of Manufacturing Science and Engineering, 141(8) (2019) 081013:1--12.

\item
Jordan, L.A., \textbf{Tschopp, M.A.}, Mlsna, T.E., Wipf, D., Horstemeyer, M.F., ``\href{https://doi.org/10.1080/1478422X.2018.1542550}{Modeling and experimental calibration of the corrosion of RHA steel in immersion and salt-fog environments},'' Corrosion Engineering, Science and Technology, 54(2) (2019) 114--121.

\item
Hern\'{a}ndez-Rivera, E., Chowdhury, S., Coleman, S.P., Ghassemi, P., \textbf{Tschopp, M.A.}$^\ast$, ``\href{https://doi.org/10.1557/mrc.2018.155}{Integrating Exploratory Data Analytics into ReaxFF Parameterization},'' MRS Communications, 8(3) (2018) 1300--1310. 

\item
{Goins, P.E.}, Murdoch, H.A., Hern\'{a}ndez-Rivera, E.,  \textbf{Tschopp, M.A.}, ``\href{https://doi.org/10.1016/j.commatsci.2018.04.034}{Effect of magnetic fields on microstructure evolution},'' Computational Materials Science, 150 (2018) 464--474.

\item
{Khanzadeh, M.}, {Chowdhury, S.},  Marufuzzaman, M., \textbf{Tschopp, M.A.}, Bian, L.,``\href{https://doi.org/10.1016/j.jmsy.2018.04.001}{Porosity Prediction: Supervised-learning of Thermal History for Direct Laser Deposition},'' Journal of Manufacturing Systems, 47 (2018) 69--82.

\item
{Chen, J.}, \textbf{Tschopp, M.A.}, Dongare, A.M., ``\href{https://doi.org/10.1063/1.5001761}{Shock Wave Propagation and Spall failure of Nanocrystalline Cu/Ta Alloys: Effect of Ta in Solid-Solution},'' Journal of Applied Physics, 122(22) (2017) 225901.

\item
{Khanzadeh, M.}, {Chowdhury, S.}, \textbf{Tschopp, M.A.}, Bian, L.,``\href{https://doi.org/10.1115/1.4038598}{Quantifying Geometric Accuracy with Unsupervised Machine Learning: Using Self-Organizing Maps on Fused Filament Fabrication Additive Manufacturing Parts},'' (ASME) Journal of Manufacturing Science and Engineering, 140 (2018) 031011.

\item
{Chen, J.}, \textbf{Tschopp, M.A.}, Dongare, A.M., ``\href{https://doi.org/10.1007/s10853-017-1879-7}{Role of Nanoscale Cu/Ta Interfaces on the Shock Compression and Spall Failure of Nanocrystalline Cu/Ta Systems at the Atomic Scale},'' Journal of Materials Science, 53 (2018) 5745--5765.

\item
{Imandoust, A.}, {Barrett, C.D.}, Al-Samman, T., \textbf{Tschopp, M.A.}, Essadiqi, E., El Kadiri, H., Hort, N., ``\href{https://www.springerprofessional.de/en/unraveling-recrystallization-mechanisms-governing-texture-develo/15502294}{Unraveling recrystallization mechanisms governing texture development from rare earth element additions to magnesium},'' Metallurgical Transactions A, 49(5) (2018) 1809--1829.

\item
Atwater, M.A., Guevara, L.N., Darling, K.A., \textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.1002/adem.201700766}{Solid State Porous Metal Production:~A Review of the Capabilities, Characteristics and Challenges},'' Advanced Engineering Materials, 20(7) (2018) 1700766:1--33.
\begin{list2}
\item[$\star$] \href{https://onlinelibrary.wiley.com/doi/abs/10.1002/adem.201870019}{Cover Image}
\item[$\star$] \href{https://onlinelibrary.wiley.com/page/journal/15272648/homepage/best-of-advanced-engineering-materials-2018.html}{Best of Advanced Engineering Materials 2018} contains articles selected by the editors to represent the most outstanding articles published throughout the past year.
\end{list2}

\item
{Foley, D.}, Tucker, G.J., \textbf{Tschopp, M.A.}, Coleman, S.P., ``\href{https://doi.org/10.1016/j.commatsci.2018.07.056}{Correlating deformation mechanisms with X-ray diffraction phenomena in nanocrystalline metals using atomistic simulations},'' Computational Materials Science, 154 (2018) 178--186.

\item
{Turnage, S.}, Darling, K.A., {Rajagopalan, M.}, Whittington, W., \textbf{Tschopp, M.A.}, Peralta, P., Solanki, K.N., ``\href{https://doi.org/10.1016/j.msea.2018.03.120}{Influence of variable processing conditions on the quasi-static and dynamic behaviors of resistance spot welded aluminum 6061-T6 sheets},'' Material Science and Engineering A, 724 (2018) 509--517.

\item
{Khanzadeh, M.}, Tian, W., Yadollahi, A., Doude, H.R., \textbf{Tschopp, M.A.}, Bian, L., ``\href{https://doi.org/10.1016/j.addma.2018.08.014}{Dual Process Monitoring of Metal-Based Additive Manufacturing Using Tensor Decomposition of Thermal Image Streams},'' Additive Manufacturing, 23 (2018) 443--456.

\item
{Banadaki, A.}, \textbf{Tschopp, M.A.}, Patala, S., ``\href{https://doi.org/10.1016/j.commatsci.2018.09.017}{An Efficient Monte-Carlo Algorithm for Determining the Minimum Energy Structures of Metallic Grain Boundaries},'' Computational Materials Science, 155 (2018) 466--475.

\item
{\textbf{Tschopp, M.A.}}, Gao, F., Solanki, K.,  ``\href{http://dx.doi.org/10.1016/j.actamat.2016.11.027}{He--V cluster nucleation and growth in $\alpha$-Fe Grain Boundaries},'' Acta Materialia, 124 (2017) 544--555.

\item
{\textbf{Tschopp, M.A.}}, {Hernandez, E.}, Darling, K.A., Atwater, M.A., Solanki, K.N., ``\href{http://dx.doi.org/10.1016/j.commatsci.2017.02.002}{A Thermodynamic and Kinetic-Based Grain Growth Model for Nanocrystalline Materials: Parameter Sensitivity Analysis and Model Extension},'' Computational Materials Science, 131 (2017) 250--265.

\item
{\textbf{Tschopp, M.A.}}, {Nouranian, S.}, Rinderspacher, C., Gwaltney, S.R., Baskes, M.I.,  Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1115/1.4037455}{Quantifying Parameter Sensitivity and Uncertainty of a Reactive Interatomic Potential for Saturated Hydrocarbons},'' ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems, 4(1) (2018) 011004:1--17.
\begin{list2}
\item[$\star$] Invited article by Sandia National Laboratory colleague in Uncertainty Quantification (DAKOTA developer)
\end{list2}

\item
{Hernandez, E.}, {Coleman, S.P.}, {\textbf{Tschopp, M.A.}}, ``\href{http://dx.doi.org/10.1021/acscombsci.6b00142}{Using Similarity Metrics to Quantify Differences in High-Throughput Datasets: Application to X-Ray Diffraction Patterns},'' ACS Combinatorial Science, 19 (2017) 25--36.
\begin{list2}
\item[$\star$] Published an ARL-TN on applying similarity/distance metrics in MATLAB and Python
\end{list2}

\item
Hornbuckle, B.C., Murdoch, H.A., Roberts, A.J., Kecskes, L.J., \textbf{Tschopp, M.A.}, Doherty, K.J., Yu, J.H., ``\href{http://dx.doi.org/10.1016/j.msea.2016.11.032}{Property Mapping of Friction Stir Welded Al-2139 T8 Plate using Site Specific Shear Punch Testing},'' MSE A, 682 (2017) 192--201.

\item
{Barrett, C.D.}, {Imandoust, A.}, Oppedal, A.L., Inal, K., \textbf{Tschopp, M.A.}, El Kadiri, H., ``\href{http://dx.doi.org/10.1016/j.actamat.2017.01.063}{Effect of Grain Boundaries on Texture Formation during Dynamic Recrystallization of Magnesium Alloys},'' Acta Materialia, 128 (2017) 270--283.

\item
{Paudel, Y.}, {Barrett, C.D.}, \textbf{Tschopp, M.A.}, Inal, K., El Kadiri, H., ``\href{https://doi.org/10.1016/j.actamat.2017.05.013}{Beyond initial twin nucleation in hcp metals: Micromechanical formulation for determining twin spacing during deformation},'' Acta Materialia, 133 (2017) 134--146.

\item
{Rajagopalan, M.}, {Adlakha, I.},  \textbf{Tschopp, M.A.}, Solanki, K.N., ``\href{https://doi.org/10.1007/s11837-017-2386-7}{Energetics of hydrogen segregation to Fe grain boundaries for modeling stress corrosion cracking},'' JOM (Journal of Materials), 69 (2017) 1398--1403. 

\item
{Aboutaleb, A.M.}, \textbf{Tschopp, M.A.}, Rao, P.K., Bian, L., ``\href{http://manufacturingscience.asmedigitalcollection.asme.org/article.aspx?articleid=2645865}{Multi-Objective Accelerated Process Optimization of Part Geometric Accuracy in Additive Manufacturing},'' ASME Journal of Manufacturing Science and Engineering, Special Issue on Data Science-Enhanced Manufacturing, 139(10) (2017) 101001--1.

\item
\textbf{Tschopp, M.A.}, {Coleman, S.P.}, McDowell, D.L., ``\href{http://dx.doi.org/10.1186/s40192-015-0040-1}{Symmetric and Asymmetric Grain Boundary Structure and Energy in Copper and Aluminum (and transferability to other FCC metals)},'' Integrating Materials and Manufacturing Innovation, 4(1) (2015) 176--189.
\begin{list2}
\item[$\star$] First Data Descriptor article in IMMI
\item[$\star$] Co-published with largest public grain boundary dataset for FCC metals (available on NIST data repository)
\item[$\star$] Highlighted by Journal Editor C.H. Ward in article ``\href{https://doi.org/10.1186/s40192-015-0041-0}{Introducing the Data descriptor article},'' IMMI 4 (2015) 190--191 as ``an excellent example of a rich and high-quality dataset that many others in the field will find useful in the conduct of their own research.''
\item[$\star$] Incorporated into new NIST Materials Data Curation System as the example for grain boundaries
\end{list2}

\item
Darling, K.A., Kapoor, M., Kotan, H., Thompson, G.B., \textbf{Tschopp, M.A.}, Kecskes, L.J., ``\href{http://dx.doi.org/10.1016/j.jnucmat.2015.09.011}{Mechanical Properties of Oxide-Dispersion-Strengthened (ODS) Ferritic Alloys Based on Zirconium Oxides},'' Journal of Nuclear Materials, 467 (2015) 205--213.

\item
{Coleman, S.P.}, {Hernandez-Rivera, E.}, Behler, K.D., Synowczynski-Dunn, J., \textbf{Tschopp, M.A.}$^\ast$, ``\href{http://dx.doi.org/10.1007/s11837-016-1856-7}{Challenges of Engineering Grain Boundaries in Boron-Based Armor Ceramics},'' JOM (Journal of Materials), 68 (2016) 1605--1615.
\begin{list2}
\item[$\star$] Invited article for issue on grain boundaries and interfaces
\end{list2}

\item
Atwater, M.A., Darling, K.A., \textbf{Tschopp, M.A.}$^\ast$, ``\href{http://dx.doi.org/10.3934/matersci.2016.2.573}{Synthesis, characterization and quantitative analysis of porous metal microstructures: Application to microporous copper produced by solid state foaming},'' AIMS Materials Science, 3(2) (2016) 573-590.
\begin{list2}
\item[$\star$] Invited article for special issue on advanced mirostructural characterization of materials
\end{list2}

\item
Bhatia, M.A., Rajagopalan, M., Darling, K.A., Tschopp, M.A., Solanki, K.N., ``\href{http://dx.doi.org/10.1080/21663831.2016.1201160}{The role of Ta on twinnability in nanocrystalline Cu-Ta alloys},'' Materials Research Letters, 5 (2017) 48--54.

\item
Nouranian, S., Gwaltney, S.R., Baskes, M.I., \textbf{Tschopp, M.A.}, Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1016/j.cplett.2015.06.071}{Nanomechanical Simulations of Tensile Bond Rupture in Single Alkane Molecules with Generalization to a Single Polyethylene Chain Using the Modified Embedded-Atom Method},'' Chemical Physics Letters, 635 (2015) 278--284.

\item
Rojhirunsakoola, T., Darling, K.A., \textbf{Tschopp, M.A.}, Pun, G.P.P., Mishin, Y., Banerjee, R., Kecskes, L.J., ``\href{http://dx.doi.org/10.1557/mrc.2015.34}{Structure and Thermal Decomposition of a Nanocrystalline Mechanically Alloyed Supersaturated Cu-Ta Solid Solution},'' MRS Communications, 5 (2015) 333--339.

\item
\textbf{Tschopp, M.A.}, Cormier, J., Feng, Q., Evans, J.L., ``\href{http://dx.doi.org/10.1007/s11661-015-2992-3}{Multiscale Microstructure, Mechanics and Prognosis of High Temperature Alloys},'' Metallurgical Transactions A, 46 (2015) 4587--4588.

\item
Darling, K.A., \textbf{Tschopp, M.A.}$^\ast$, Liu, Z.K., ``\href{http://dx.doi.org/10.1016/j.commatsci.2015.04.052}{Rebuttal Comments on ``Mitigating grain growth in binary nanocrystalline alloys through solute selection based on thermodynamic stability maps}'','' Computational Materials Science, 107 (2015) 238--242.

\item
{Coleman, S.P.}, \textbf{Tschopp, M.A.}, Weinberger, C.R., Spearot, D.E., ``\href{http://dx.doi.org/10.1007/s10853-015-9087-9}{Bridging atomistic simulations and experiments via virtual diffraction: Understanding homophase grain boundary and heterophase interface structures},'' Journal of Materials Science, 51 (2016) 1251--1260.

\item
\textbf{Tschopp, M.A.}, Miller, J., Oppedal, A., Solanki, K.N., ``\href{http://dx.doi.org/10.1007/s11661-015-2964-7}{Evaluating local primary dendrite arm spacing characterization techniques using synthetic directionally-solidified dendritic microstructures},'' Metallurgical Transactions A, 46 (2015) 4610--4628.

\item
Atwater, M.A., Darling, K.A., \textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.1002/adem.201500063}{Solid-state foaming by oxide reduction and expansion: Tailoring the foamed metal microstructure in the Cu--CuO system with oxide content and annealing conditions},'' Advanced Engineering Materials, 18(1) (2016) 83--95.

\item
{Adlakha, I.}, Solanki, K.N., \textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.1016/j.msea.2014.08.083}{The role of grain boundary structure and crystal orientation on crack growth asymmetry in aluminum},'' Materials Science and Engineering A, 618 (2014) 345-354.

\item
{Adlakha, I.}, {Bhatia, M.A.}, \textbf{Tschopp, M.A.}, Solanki, K.N.,  ``\href{http://dx.doi.org/10.1080/14786435.2014.961585}{Atomic scale investigation of grain boundary structure role on intergranular deformation in aluminium},'' Philosophical Magazine, 94 (2014) 3445--3466.

\item
van Beers, P.R.M., Kouznetsova, V.G., Geers, M.G.D., \textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.doi.org/10.1016/j.actamat.2014.08.045}{A multi-scale model of grain boundary structure and energy: From atomistic to continuum description},'' Acta Materialia, 82 (2015) 513--529.
\begin{list2}
\item[$\star$] ``Furthermore, I would like to direct acknowledgements to Mark Tschopp and David McDowell for their constructive help, insight and contributions to the third chapter," in ``Multiscale modelling of grain boundary plasticity" by Paul van Beers, dissertation, Technische Universiteit Eindhoven (2015).
\end{list2}

\item
\textbf{Tschopp, M.A.}, Gao, F., Solanki, K.N., ``\href{http://dx.doi.org/10.1063/1.4883357}{Binding of He$_n$V Clusters to $\alpha$-Fe Grain Boundaries},'' Journal of Applied Physics, 115 (2014) 233501.

\item
Darling, K.A., \textbf{Tschopp, M.A.}$^\ast$, Guduru, R.K., Yin, W.H., Wei, Q., Kecskes, L.J., ``\href{http://dx.doi.org/10.1016/j.actamat.2014.04.074}{Microstructure and Mechanical Properties of Bulk Nanostructured Cu-Ta Alloys Consolidated by Equal Channel Angular Extrusion},'' Acta Materialia, 76 (2014) 168--185.

\item
\textbf{Tschopp, M.A.}, Murdoch, H.A., Kecskes, L.J., Darling, K.A., ``\href{http://dx.doi.org/10.1007/s11837-014-0978-z}{``Bulk'' Nanocrystalline Metals: Review of the Current State of the Art and Future Opportunities for Copper and Copper Alloys},'' JOM (Journal of Materials), 66 (2014) 1000--1019.

\item
Shang, S.L., Wang, Y., Du, Y., \textbf{Tschopp, M.A.}, Liu, Z.K., ``\href{http://dx.doi.org/10.1016/j.commatsci.2014.04.040}{Integrating computational modeling and first-principles calculations to predict the stacking fault energy for dilute multicomponent Ni-base alloys},'' Computational Materials Science, 91 (2014) 50--55.

\item
{Rajagopalan, M.}, {Bhatia, M.A.}, Solanki, K.N., \textbf{Tschopp, M.A.}, Srolovitz, D., ``\href{http://dx.doi.org/10.1016/j.actamat.2014.04.011}{Role of atomistic-scale energetics on liquid-metal embrittlement of aluminum due to gallium},'' Acta Materialia, 73 (2014) 312--325.

\item
{Liyanage, L.}, Houze, J., Kim, S., \textbf{Tschopp, M.A.}, Kim, S-G., Baskes, M.I., Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1103/PhysRevB.89.094102}{Structural, elastic and thermal properties of cementite (Fe$_3$C) calculated using Modified Embedded Atom Method},'' Physical Review B, 89 (2014) 094102.
\begin{list2}
\item[$\star$] Fe--C Potential published, \href{http://www.ctcms.nist.gov/potentials/Fe-C.html}{NIST potential site}
\end{list2}

\item
{Nouranian, S.}, \textbf{Tschopp, M.A.}, Gwaltney, S.R., Baskes, M.I.,  Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1039/c4cp00027g}{A Reactive Interatomic Potential for the Molecular Dynamics Simulations of Saturated Hydrocarbons Using the Modified Embedded-Atom Method},'' Physical Chemistry Chemical Physics, 16 (2014) 6233--6249.

\item
{Asadi, E.}, Zaeem, M.A., Moitra, A., \textbf{Tschopp, M.A.}$^\ast$, ``\href{http://dx.doi.org/10.1088/0953-8984/26/11/115404}{Effects of Vacancy Defects on Generalized Stacking Fault Energy of FCC metals},'' Journal of Physics: Condensed Matter, 26 (2014) 115404.
\begin{list2}
\item[$\star$] IOP Select Article
\end{list2}

\item
Zimmerman, J., Sabau, A., Zaeem, M.A., Tschopp, M., Spearot, D., ``\href{http://dx.doi.org/10.1007/s11837-013-0846-2}{Algorithm Development in Computational Materials},'' Journal of Materials, 66 (2014) 397--398.

\item
\textbf{Tschopp, M.A.}, Gao, F., Yang, L., Solanki, K.N., ``\href{http://dx.doi.org/10.1063/1.4861719}{Binding Energetics of Substitutional and Interstitial Helium and Di-Helium Defects with Grain Boundary Structure in $\alpha$-Fe},'' Journal of Applied Physics, 115 (2014) 033503:1--16.

\item
Atwater, M.A., Darling, K.A., \textbf{Tschopp, M.A.}$^\ast$, ``\href{http://dx.doi.org/10.1002/adem.201300431}{Towards reaching the theoretical limit of porosity in conventional solid state metal foams: Intraparticle expansion as a primary and additive means to create porosity},'' Advanced Engineering Materials, 16 (2014) 190--195.
\begin{list2}
\item[$\star$] \href{http://onlinelibrary.wiley.com/doi/10.1002/adem.201470006/pdf}{Cover Image}
\item[$\star$] ``\href{http://www.materialsviews.com/aero-a-new-method-for-creating-metal-foams/}{AERO: a new method for creating metal foams},'' Materials Views, January 30, 2014.
\item[$\star$] ``\href{http://blogs.millersville.edu/exchange/2014/02/20/using-nanotechnology-to-create-metal-foams/}{Using Nanotechnology to Create Metal Foams},'' Millersville University press release, February 20, 2014.
\item[$\star$] \href{http://onlinelibrary.wiley.com/store/10.1002/adem.201300431/asset/supinfo/adem201300431-sm-0001-SuppFig-S1.gif?v=1&s=2410042c646030030c12bb1c065d433cecdad07d}{Sectioned Particle Video}.
\end{list2}

\item
Darling, K.A., \textbf{Tschopp, M.A.}$^\ast$, Atwater, M.A., VanLeeuwen, B.K., Liu, Z.K., ``\href{http://dx.doi.org/10.1016/j.commatsci.2013.10.018}{Mitigating grain growth in binary nanocrystalline alloys through solute selection based on thermodynamic stability maps},'' Computational Materials Science, 84 (2014) 255--266.

\item
{Eshraghi, M.}, \textbf{Tschopp, M.A.}, Zaaem, M.A., Felicelli, S.D., ``\href{http://dx.doi.org/10.1016/j.matdes.2013.11.026}{Effect of resistance spot welding parameters on weld pool properties in a DP600 dual-phase steel: A parametric study using thermomechanically-coupled finite element analysis},'' Materials and Design, 56 (2014) 387--397.

\item
Darling, K.A., \textbf{Tschopp, M.A.}, Roberts, A.J., Armstrong, L., Kapoor, D., Mathaudhu, S.N., Kecskes, L., ``\href{http://dx.doi.org/10.1016/j.msea.2013.09.047}{Influence of Mn Solute Content on Grain Size Reduction and Improved Strength in Mechanically Alloyed Al-Mn Alloys},'' Materials Science and Engineering A, 589 (2014) 57--65.

\item
\textbf{Tschopp, M.A.}, Miller, J.D., {Oppedal, A.L.}, Solanki, K.N., ``\href{http://dx.doi.org/10.1007/s11661-013-1985-3}{Characterizing the local primary dendrite arm spacing in directionally-solidified dendritic microstructures},'' Metallurgical Transactions A 45(1) (2014) 426--437.
\begin{list2}
\item[$\star$] Editor's Choice Article
\item[$\star$]
``\href{https://www.cavs.msstate.edu/story.php?d=387}{CAVS Studies High Temperature Aerospace Materials in Modern Turbine Engines},'' MSU CAVS press release, December 6, 2013.
\item[$\star$] Nominated for Howe Medal Award in ASM International
\end{list2}

\item
{Rajagopalan, M.}, \textbf{Tschopp, M.A.}, Solanki, K.N.,  ``\href{http://dx.doi.org/10.1007/s11837-013-0807-9}{Grain boundary segregation of interstitial and substitutional impurity atoms in alpha-iron},'' JOM (Journal of Materials), 66 (2014) 129-138.

\item
El Kadiri, H., {Barrett, C.D.}, \textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.1016/j.actamat.2013.09.002}{The candidacy of shuffle and shear during compound twinning in hexagonal close-packed structures},'' Acta Materialia 61 (2013) 7646--7659.

\item
Darling, K.A., \textbf{Tschopp, M.A.}$^\ast$, Roberts, A.J., Ligda, J.P., Kecskes, L.J., ``\href{http://dx.doi.org/10.1016/j.scriptamat.2013.05.036}{Enhancing the grain refinement in polycrystalline materials using surface mechanical attrition treatment at cryogenic temperatures},'' Scripta Materialia, 69 (2013) 461--464.

\item
{Deng, X.}, {Potula, S.}, Grewal, H., Solanki, K.N., \textbf{Tschopp, M.A.}, Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1016/j.aap.2013.03.016}{Finite Element Analysis Head Injury Study: Parametric Effects on the Side curtain airbag deployment interaction with a dummy head in a side impact crash},'' Accident Analysis \& Prevention 55 (2013) 232-241.

\item
{Rhodes, N.R.}, \textbf{Tschopp, M.A.}$^\ast$, Solanki, K.N., ``\href{http://dx.doi.org/10.1088/0965-0393/21/3/035009}{Quantifying the Energetics of Carbon Segregation to Fe Symmetric Tilt Grain Boundaries Using Atomistic Simulations},'' Modeling and Simulation in Materials Science and Engineering, 21(3) (2013) 035009.
\begin{list2}
\item[$\star$] \href{http://ej.iop.org/pdf/msmse/covers/21/MSMSE_21_3_cover.pdf}{Cover image}.
\end{list2}

\item
{Zhang, X.}, \textbf{Tschopp, M.A.}, Horstemeyer, M.F., Shi, S.Q., Cao, J., ``Mechanical properties of amorphous cellulose using molecular dynamics simulations with a reactive force field,'' International Journal of Modelling, Identification and Control, 18(3) (2013) 211--217.

\item
Bouvard, J.L., Francis, D.K., \textbf{Tschopp, M.A.}, Marin, E.B., Bammann, D.J., Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1016/j.ijplas.2012.10.005}{An internal state variable material model for predicting the time, thermomechanical, and stress state dependence of amorphous glassy polymers under large deformation},'' International Journal of Plasticity, 42 (2013) 168--193.

\item
Solanki, K.N., \textbf{Tschopp, M.A.}, {Bhattia, M.A.}, {Rhodes, N.R.}, ``\href{http://dx.DOI.org/10.1007/s11661-012-1430-z}{Nanoscale Investigation of Role of Grain Boundary Character on Hydrogen Segregation and Embrittlement in $\alpha$-Fe},'' Metallurgical and Materials Transactions A, 44 (2013) 1365--1375.

\item
{Bhattia, M.A.}, Solanki, K.N., Moitra, A., \textbf{Tschopp, M.A.}$^\ast$, ``\href{http://dx.DOI.org/10.1007/s11661-012-1082-z}{Investigating damage evolution at the nanoscale: Molecular dynamics simulations of nanovoid growth in single crystal aluminum},'' Metallurgical and Materials Transactions A, 44 (2013) 617--626.

\item
{Barrett, C.D.}, \textbf{Tschopp, M.A.}$^\ast$, El Kadiri, H., ``\href{http://dx.DOI.org/10.1016/j.jmps.2012.06.015}{Breakdown of the Schmid Law in Homogeneous and Heterogeneous Nucleation Events of Slip and Twinning in Magnesium},'' Journal of the Mechanics and Physics of Solids, 60 (2012) 2084--2099.

\item
{Potula, S.}, Solanki, K.N., Oglesby, D.L., \textbf{Tschopp, M.A.}, Bhattia, M.A., ``\href{http://dx.DOI.org/10.1016/j.aap.2012.03.007}{Investigating occupant injuries and safety through simulating the interaction between side curtain airbag deployment and an out-of-position occupant},'' Accident Analysis and Prevention, 49 (2012) 392--403.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Baskes, M.I., Gao, F., Sun, X., Khaleel, M., Horstemeyer, M.F., ``\href{http://dx.DOI.org/10.1016/j.jnucmat.2011.08.003}{Generalized framework for interatomic potential design: Application to the Fe-He system},'' Journal of Nuclear Materials, 425 (2012) 22--32.

\item
{Barrett, C.D.}, \textbf{Tschopp, M.A.}$^\ast$, El Kadiri, H., ``\href{http://dx.DOI.org/10.1016/j.scriptamat.2012.01.034}{Automated analysis of twins in hexagonal close-packed metals using molecular dynamics},'' Scripta Materialia, 66 (2012) 666--669.
\begin{list2}
\item[$\star$] \href{http://lammps.sandia.gov/doc/compute_basal_atom.html}{`compute basal/atom' implemented into LAMMPS}
\end{list2}

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Gao, F., Sun, X., Khaleel, M., Horstemeyer, M.F., ``\href{http://dx.DOI.org/10.1103/PhysRevB.85.064108}{Probing grain boundary sink strength at the nanoscale: Energetics and length scales of vacancy and interstitial absorption by grain boundaries in $\alpha$-Fe},'' Physical Review B, 85 (2012) 064108.
\begin{list2}
\item[$\star$] ``{CAVS studies radiation effects on nuclear reactor materials},'' MSU press release, March 09, 2012.
\end{list2}

\item
Li, D.S., \textbf{Tschopp, M.A.}$^\ast$, Khaleel, M., Sun, X., ``\href{http://dx.DOI.org/10.1016/j.commatsci.2011.07.056}{Comparison of reconstructed spatial microstructure images using different statistical descriptors},'' Computational Materials Science, 51 (2012) 437--444.
\begin{list2}
\item[$\star$] PNNL Research Highlight, FEB 2012, ``\href{http://www.pnnl.gov/science/highlights/highlight.asp?id=1115}{Learning About Material Integrity from Statistical Data: Imaging, statistics, and computational analysis shed new light on defects}''.
\end{list2}

\item
{Zhang, X.E.}, \textbf{Tschopp, M.A.}, Shi, S.Q., Cao, J., ``Molecular Dynamics Simulations of the Glass Transition Temperature of Amorphous Cellulose,'' Applied Mechanics and Materials, 214 (2012) 7--11, DOI:10.4028/www.scientific.net/AMM.214.7.

\item
{Lugo, M.}, Jordan, J.B., Horstemeyer, M.F., \textbf{Tschopp, M.A.}, Harris, J., Gokhale, A., ``\href{http://dx.DOI.org/10.1016/j.msea.2011.05.017}{Quantification of Damage Evolution in a 7075 Aluminum Alloy using an Acoustic Emission Technique},'' Materials Science and Engineering A, 528 (2011) 6708--6714. 

\item
{Lugo, M.}, \textbf{Tschopp, M.A.}, Jordan, J.B., Horstemeyer, M.F., ``\href{http://dx.DOI.org/10.1016/j.scriptamat.2011.01.029}{Microstructure and Damage Evolution during Tensile Loading of AZ61 Magnesium Alloy},'' Scripta Materialia, 64 (2011) 912--915.

\item
\textbf{Tschopp, M.A.}, Horstemeyer, M.F., Gao, F., Sun, X., Khaleel, M., ``\href{http://dx.DOI.org/10.1016/j.scriptamat.2011.01.031}{Energetic driving force for preferential binding of self-interstitial atoms to Fe grain boundaries over vacancies},'' Scripta Materialia, 64 (2011) 908--911.

\item
\textbf{Tschopp, M.A.}, Wilks, G.B., Spowart, J.E., ``\href{http://dx.DOI.org/10.1115/1.4002639}{Multiscale Characterization of Chemically Reactive Multiphase Composite Microstructures},'' Journal of Engineering Materials and Technology (special issue on Recent Advances on Composites and Heterogeneous Materials), 133 (2011) 011004. 

\item
{Hossain, D.}, \textbf{Tschopp, M.A.}$^\ast$, Ward, D.K., Bouvard, J.L., Wang, P., Horstemeyer, M.F., ``\href{http://dx.DOI.org/10.1016/j.polymer.2010.10.009}{Molecular dynamics simulations of deformation mechanisms of amorphous polyethylene},'' Polymer, 51 (2010) 6071--6083.

\item
\textbf{Tschopp, M.A.}, Groeber, M.A., Simmons, J., Rosenberger, A.H., Woodward, C., ``\href{http://dx.DOI.org/10.1016/j.matchar.2010.10.008}{Automated Extraction of Symmetric Microstructure Features in Serial Sectioning Images},'' Materials Characterization, 61 (2010) 1406--1417.

\item 
\textbf{Tschopp, M.A.}, Tiley, J.S., Viswanathan, G.B., ``\href{http://dx.DOI.org/10.1179/026708309X12560332736638}{Automated Identification and Characterization of Secondary \& Tertiary $\gamma\prime$ Precipitates in Nickel-based Superalloys},'' Materials Science \& Technology, 26(12) (2010) 1414--1422.  

\item 
Tucker, G.J., \textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.actamat.2010.08.008}{Evolution of Structure and Free Volume in Symmetric Tilt Boundaries during Deformation using Atomistic Simulations},'' Acta Materialia, 58 (2010) 6464--6473.

\item 
Wilks, G.B., \textbf{Tschopp, M.A.}, Spowart, J.E., ``\href{http://dx.DOI.org/10.1016/j.msea.2009.09.003}{Multi-Scale Characterization of Inhomogeneous Morphologically Textured Microstructures},'' Materials Science \& Engineering A, 527 (2010) 883--889.

\item 
\textbf{Tschopp, M.A.}, Groeber, M.A., Fahringer, R., Simmons, J., Rosenberger, A.H., Woodward, C., ``\href{http://dx.DOI.org/10.1016/j.scriptamat.2009.10.038}{Symmetry-Based Automated Extraction of Microstructural Features: Application to Dendritic Cores in Single Crystal Ni-Based Superalloys},'' Scripta Materialia, 62 (2010) 357--360.

\item 
\textbf{Tschopp, M.A.}, Groeber, M.A., Fahringer, R., Simmons, J., Rosenberger, A.H., Woodward, C., ``\href{http://dx.DOI.org/10.1088/0965-0393/18/2/025014}{Automated Detection and 3D Characterization of Microstructural Features: Application to Eutectic Particles in Single Crystal Ni-Based Superalloys},'' Modelling and Simulation in Materials Science \& Engineering, 18 (2010) 025014.
\begin{list2}
\item[$\star$] {MSMSE Featured Article}
\end{list2}

\item
Tiley, J.S., Rajagopolan, S., Viswanathan, G.B., Shiveley, A., \textbf{Tschopp, M.A.}, Banerjee, R., Fraser, H.L., ``\href{http://dx.DOI.org/10.1016/j.micron.2010.03.003}{Measurement of $\gamma\prime$ Precipitates in a Nickel-based Superalloy using Energy-Filtered Transmission Electron Microscopy coupled with Automated Segmenting Techniques},'' Micron, 41(6) (2010) 641--647.

\item 
\textbf{Tschopp, M.A.}, Bartha, B.B., Porter, W.J., Murray, T., Fairchild, S., ``\href{http://dx.DOI.org/10.1007/s11661-009-9938-6}{Microstructure - dependent local strain behavior in polycrystals through in situ scanning electron microscope tensile experiments},'' Metallurgical Transactions A, 40 (2009) 2363--2368.

\item 
Spearot, D.E., \textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.scriptamat.2008.12.037}{Orientation and Rate Dependence of Dislocation Nucleation Stresses computed using Molecular Dynamics},'' Scripta Materialia, 60 (2009) 675--678.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.ijplas.2007.02.010}{Dislocation nucleation in $\Sigma3$ asymmetric tilt grain boundaries},'' International Journal of Plasticity, 24 (2008) 191--217.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.scriptamat.2007.10.010}{Grain boundary dislocation sources in nanocrystalline copper},'' Scripta Materialia, 58 (2008) 299--302.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.jmps.2007.11.012}{Influence of single crystal orientation on homogeneous dislocation nucleation under uniaxial loading},'' Journal of Mechanics and Physics of Solids, 56 (2008) 1806--1830.

\item 
\textbf{Tschopp, M.A.}, Tucker, G.J., McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.commatsci.2008.03.041}{Atomistic simulations of tension-compression asymmetry in dislocation nucleation for copper grain boundaries},'' Computational Materials Science, 44 (2008) 351--362.

\item 
\textbf{Tschopp, M.A.}, Wilks, G.B., Spowart, J.E., ``\href{http://dx.DOI.org/10.1088/0965-0393/16/6/065009}{Multi-Scale Characterization of Orthotropic Microstructures},'' Modelling and Simulation in Materials Science and Engineering, 16 (2008) 065009.

\item 
Spearot, D.E., \textbf{Tschopp, M.A.}, Jacob, K.I., McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.actamat.2006.08.060}{Tensile strength of $\left\langle 100\right\rangle$ and $\left\langle 110\right\rangle$ tilt bicrystal copper interfaces},'' Acta Materialia, 55 (2007) 705--714.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1063/1.2715137}{Tension-compression asymmetry in homogeneous dislocation nucleation in single crystal copper},'' Applied Physics Letters, 90 (2007) 121916.

\item 
\textbf{Tschopp, M.A.}, Tucker, G.J., McDowell, D.L., ``\href{http://dx.DOI.org/10.1016/j.actamat.2007.03.012}{Structure and free volume of $\left\langle 110\right\rangle$ symmetric tilt grain boundaries with the E structural unit},'' Acta Materialia, 55 (2007) 3959--3969.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1080/14786430701255895}{Structures and energies of $\Sigma3$ asymmetric tilt grain boundaries in Cu and Al},'' Philosophical Magazine, 87 (2007) 3147--3173.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1007/s10853-007-1626-6}{Structural unit and faceting description of $\Sigma3$ asymmetric tilt grain boundaries},'' Journal of Materials Science, 42(18) (2007) 7806--7811.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.DOI.org/10.1080/14786430701455321}{Asymmetric tilt grain boundary structure and energy in copper and aluminum},'' Philosophical Magazine, 87(25) (2007) 3871--3892.

\item 
\textbf{Tschopp, M.A.}, Spearot, D.E., McDowell, D.L., ``\href{http://dx.DOI.org/10.1088/0965-0393/15/7/001}{Atomistic simulations of homogeneous dislocation nucleation in single crystal copper},'' Modelling and Simulation in Materials Science and Engineering, 15 (2007) 693--709.

\item 
\textbf{Tschopp, M.A.}, Wang, Q.G., DeWyse, M.J., ``{Mechanisms of Misrun Formation in Aluminum Lost Foam Castings},'' Transactions of the American Foundry Society, 110 (2002) 1371--1386. 

\item 
\textbf{Tschopp, M.A.}, ``{Fluidity of Aluminum A356 in the Lost Foam Casting Process},'' Transactions of the American Foundry Society, 110 (2002) 1387--1397. 

\item 
Bennett, S., \textbf{Tschopp, M.A.}, Vrieze, A., Zelkovich, E., Ramsay, C.W., Askeland, D.R., ``{Observations on the Effect of Gating Design on Metal Flow and Defect Formation in Aluminum Lost Foam Castings: Part I},'' Transactions of the American Foundry Society, 109 (2001) 1473--1487.

\item 
\textbf{Tschopp, M.A.}, Ramsay, C.W., Askeland, D.R., ``{Mechanisms of Formation of Pyrolysis Defects in Aluminum Lost Foam Castings},'' Transactions of the American Foundry Society, 108 (2000) 609--614.
\begin{list2}
\item[$\star$] {Best Paper Award}
\end{list2}

\item 
\textbf{Tschopp, M.A.}, Ramsay, C.W., Askeland, D.R., ``Processing Variable Significance on Metal Flow and Defect Formation in Thick Section LFCs - Full Factorial Experiment,'' Transactions of the American Foundry Society, 108 (2000) 267--274. 

\end{cvlist}

