\section{\sc Thesis and Dissertation}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item 
\textbf{Tschopp, M.A.}, ``\href{http://hdl.handle.net/1853/16239}{Atomistic simulations of dislocation nucleation in single crystals and grain boundaries},'' Ph.D. Dissertation, Georgia Institute of Technology, pp.\ 1--375 (2007) DOI: 1853/16239.
\begin{list2}
\item[$\star$] 2008 Sigma Xi Best PhD Thesis Award
\end{list2}

\item 
\textbf{Tschopp, M.A.}, ``Mechanisms of the Formation of Pyrolysis Defects in Aluminum Lost Foam Castings,'' M.S. Thesis, University of Missouri-Rolla, pp.\ 1--255 (1999).

\end{cvlist}

\section{\sc Refereed Book Chapters}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Horstemeyer, M.F., ``A Generalized Framework for Quantifying Material Structure-Property Relationships and Uncertainties: Applicability to ICME,'' \href{http://www.asminternational.org/portal/site/www/AsmStore/ProductDetails/?vgnextoid=98e8444762db0310VgnVCM100000621e010aRCRD#details}{\textbf{\textit{Tools Developed and Needed to Realize the Vision of Integrated Computational Materials Engineering}}}, ed. S. Arnold \& T. Wong, ASM International, 2011.

\item 
\textbf{Tschopp, M.A.}, Spearot, D.E., McDowell, D.L., ``\href{http://dx.doi.org/10.1016/S1572-4859(07)00002-2}{Influence of Grain Boundary Structure on Dislocation Nucleation in FCC Metals},'' \textbf{\textit{Dislocations in Solids}}, \textit{A Tribute to F.R.N. Nabarro}, ed. J.P.~Hirth, vol. 14, pp.~43--139 (2008).

\end{cvlist}

\section{\sc Patents}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
Atwater, M.A., Darling, K.A., \textbf{Tschopp, M.A.}, ``\href{https://patents.google.com/patent/US20200024692A1/en}{Method of creating porous structures by particle expansion},'' US Patent App.~16/241,345.

\end{cvlist}

