\section{\sc Refereed Conference Papers}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
Seifi, S.H., Tian, W., Doude, H., \textbf{Tschopp, M.A.}, Bian, L., ``Layer-wise Profile Monitoring of Laser-based Additive Manufacturing,'' SFF 2018.

\item
{Khanzadeh, M.}, Chowdhury, S., \textbf{Tschopp, M.A.}, Bian, L., ``Predicting Porosity in Additive Manufacturing Using Image Processing of Melt Pool Profiles,'' Proceedings of the 12th Manufacturing Science and Engineering Conference, MSEC 2017.

\item
{Aboutaleb, A.M.}, Bian, L., Rao, P.K., \textbf{Tschopp, M.A.}, ``Accelerated Geometry Accuracy Optimization of Additive Manufacturing,'' Proceedings of the 12th Manufacturing Science and Engineering Conference, MSEC 2017.

\item
{Khanzadeh, M.}, Chowdhury, S., \textbf{Tschopp, M.A.}, Bian, L., ``Using Melt Pool Thermal Profiles to Predict Porosity in Additive Manufacturing,'' 2017 Industrial and Systems Engineering Research Conference (ISERC).
\begin{list2}
\item[$\star$] 2017 ISERC Best Student Paper Award.
\end{list2}

\item
Dunn, J.S., Coleman, S.P., \textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.1002/9781119321811.ch17}{First Principles Study of Defect Formation in Bulk B$_6$O},'' Developments in Strategic Ceramic Materials II: Ceramic Engineering and Science Proceedings,  Volume 37(7), John Wiley \& Sons, 2017, 181--188.

\item
Atwater, M.A., Darling, K.A., \textbf{Tschopp, M.A.}, ``Solid State Foaming of Metals via Powder Metallurgy and Additive Expansion through the Reduction of Oxides,'' Powder Metallurgy Conference Paper, 2016.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., ``Integrated Computational Materials Engineering (ICME) of Nanostructured Metal Feed Stocks for Powder Metallurgy,'' Powder Metallurgy Conference Paper, 2016.

\item
Darling, K.A., Roberts, A.J., Catalano, J.E., \textbf{Tschopp, M.A.}, Kecskes, L.J., ``Effect of Processing Parameters on the Microstructure of Mechanically Alloyed Nanostructured Al--Mn Alloys,'' 2015 TMS Proceedings:Advanced Composites for Aerospace, Marine, and Land Applications II, 1--11.

\item
{Rajagopalan, M.}, {Bhatia, M.}, Solanki, K., Tschopp, M., ``Investigation of atomic-scale energetics on liquid metal embrittlement of aluminum due to gallium,'' 2014 TMS Annual Meeting Supplemental Proceedings, Solid-State Interfaces III, p.~1069--1076.

\item
{Turnage, S.A.}, Solanki, K.N., Whittington, W.R., Florea, R.S., \textbf{Tschopp, M.A.}, Darling, K.A., ``Tensile and shear mechanical properties in a thermo-mechanical-electrical processed spot weld,'' 2014 TMS Proceedings, Light Metals 2014, p.~359--363.

\item
{Eshraghi, M.}, \textbf{Tschopp, M.A.}, Zaaem, M.A., Felicelli, S.D., ``A parametric study of resistance spot welding of a dual-phase steel using finite element analysis,'' 8th Pacific Rim International Conference on Advanced Materials and Processing (PRICM-8).

\item
\textbf{Tschopp, M.A.}, Oppedal, A.L., Miller, J.D., Groeber, M.A., Rosenberger, A.H., Solanki, K.N., ``\href{http://dx.doi.org/10.1002/9781118659045.ch35}{Characterizing Primary Dendritic Microstructures to Quantify the Processing-Structure-Property Relationship In Single Crystal Nickel-Based Superalloys},'' Characterization of Minerals, Metals and Materials 2013, John Wiley \& Sons, Inc., p.~301--310 (2013).

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Gao, F., Sun, X., ``Energetics and length scales of point defect and element segregation to grain boundaries in $\alpha$-Fe,'' Modeling and Experimental Validation of Multiscale Mechanical Behavior from Atomic Scale to Macro Scale, 2013 TMS Annual Meeting \& Exhibition.

\item
{Adlakha, I.}, Solanki, K.N., \textbf{Tschopp, M.A.}, ``Influence of grain boundary structure on interfacial fracture under tensile loading: Cohesive zone model informed by atomistic simulations,'' 2013 TMS Annual Meeting \& Exhibition.

\item 
Bouvard, J.-L., Bouvard, C., Denton, B., {\textbf{Tschopp, M.A.}},  Horstemeyer, M.F., ``\href{http://dx.doi.org/10.1007/978-1-4614-0213-8_21}{Simulation of Impact Tests on Polycarbonate at Different Strain Rates and Temperatures},'' Conference Proceedings of the Society for Experimental Mechanics Series, 2011, p.~145--147.

\item
{Zhang, X.E.}, \textbf{Tschopp, M.A.}, Shi, S., Cao, J., ``Molecular Dynamics Simulations of Deformation in Amorphous Cellulose,'' Proceedings of 12$^{th}$  International Conference on Wood \& Biofiber Plastic Composites and Nanotechnology in Wood Composites Symposium.

\item 
{Barrett, C.D.}, {\textbf{Tschopp, M.A.}}, El Kadiri, H., Li, B., ``\href{http://dx.doi.org/10.1002/9781118062029.ch56}{Influence of Crystallographic Orientation on Twin Nucleation in Single Crystal Magnesium},'' in Magnesium Technology 2011 (eds W.H. Sillekens, S.R. Agnew, N.R. Neelameggham and S.N. Mathaudhu), John Wiley \& Sons, Inc., Hoboken, NJ, USA.

\item
{Lugo, M.}, Jordan, J.B., Horstemeyer, M.F., \textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.1002/9781118062029.ch66}{Microstructure relationship in the damage evolution process of an AZ61 magnesium alloy},'' in Magnesium Technology 2011 (eds W.H. Sillekens, S.R. Agnew, N.R. Neelameggham and S.N. Mathaudhu), John Wiley \& Sons, Inc., Hoboken, NJ, USA.

\item
{\textbf{Tschopp, M.A.}}, Ward, D.K., Bouvard, J.L., Horstemeyer, M.F., ``Atomic Scale Deformation Mechanisms of Amorphous Polyethylene under Tensile Loading,'' Massively Parallel Simulations of Materials Response symposium, TMS Annual Meeting 2011, p.~789--794.

\item
{Bhattia, M.A.}, Solanki, K.N., Moitra, A., \textbf{Tschopp, M.A.}, ``The effect of crystallographic orientation on void growth: A molecular dynamics study,'' Deformation, Damage, and Fracture of Light Metals and Alloys symposium, TMS Annual Meeting 2011, p.~577--584.

\item
\textbf{Tschopp, M.A.}, Horstemeyer, M.F., ``Computational framework for assessing grain boundary structure-property relationships at the nanoscale,'' Tools Developed and Needed to Realize the Vision of Integrated Computational Materials Engineering Symposium, Materials Science and Technology Conference and Exhibition 2010, p.~1138--1143 .

\item
\textbf{Tschopp, M.A.}, Horstemeyer, M.F., Gao, F., Sun, X., Khaleel, M., ``Influence of grain boundary character on point defect formation energies in BCC Fe,'' Phase Stability, Diffusion, Kinetics and Their Applications (PSDK-V) Symposium, Materials Science and Technology Conference and Exhibition 2010, p.~989--999.

\item
{Bhatia, M.A.}, \textbf{Tschopp, M.A.}, Solanki, K., Horstemeyer, M.F., ``Influence of crystallographic orientation on void growth in Al,'' Multi Scale Modeling of Microstructure Deformation in Material Processing Symposium, Materials Science and Technology Conference and Exhibition 2010, p.~924--933.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Atomistic Simulations of Dislocation Nucleation in FCC Metals,'' Atomistic Fracture and Deformation, $12^{th}$ International Conference on Fracture 2009.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Atomistic simulations of grain boundary dislocation nucleation,'' Advances in Heterogeneous Material Mechanics 2008 - Proceedings of the 2nd International Conference on Heterogeneous Material Mechanics, ICHMM 2008, p.~97--104.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``{Atomistic simulations of grain boundary dislocation nucleation},'' Hael Mughrabi Symposium, TMS Annual Meeting 2008, p.~29--34.

\item 
Tucker, G.J., \textbf{Tschopp, M.A.}, McDowell, D.L., ``Atomistic simulations of dislocation nucleation in copper grain boundaries under uniaxial tension and compression,'' Hael Mughrabi Symposium, TMS Annual Meeting 2008, p.~141--146.

\item 
\textbf{Tschopp, M.A.}, Tiwari, S., Ghosh, S., McDowell, D.L., ``{Influence of Grain Boundary Character on Nanocrystalline Plasticity in Copper},'' Hael Mughrabi Symposium, TMS Annual Meeting 2008, p.~215--220.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``{Structures, energies and dislocation nucleation behaviours of $\Sigma3$ asymmetric tilt grain boundaries},'' Plasticity From the Atomic Scale to Constitutive Laws, TMS Annual Meeting 2007, p.~23--32.

\item 
\textbf{Tschopp, M.A.}, Tucker, G.J., McDowell, D.L., ``{Atomistic simulations of free volume in $\left\langle 100\right\rangle$ and $\left\langle 110\right\rangle$ symmetric tilt grain boundaries in Cu and Al},'' Plasticity From the Atomic Scale to Constitutive Laws,  TMS Annual Meeting 2007, p.~33--42.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Dislocation nucleation in asymmetric tilt grain boundaries,'' 2007 International Symposium on Plasticity.

\item 
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.doi.org/10.1007/1-4020-4972-2_325}{Microrotation-Augmented Energy Minimization for Generating Nanocrystalline Materials},'' Proceedings of the $16^{th}$ European Conference of Fracture, Emmanuel Gdoutos (Editor), (2006).

\item 
\textbf{Tschopp, M.A.}, Tucker, G.J., McDowell, D.L., ``{Atomistic Modeling of Grain Boundary Structure and Dislocation Emission},'' Progress and Challenges in Understanding Materials Interfaces, Lawrence Cook, Wayne Kaplan (Editors), Materials Science and Technology Conference and Exhibition 2006.


\end{cvlist}

 