\section{\sc Technical Reports}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Tschopp, M.A.}, Cassenti, D.N., ``\href{https://doi.org/10.5281/zenodo.18443859}{The Army Artificial Intelligence Innovation Institute (Summary Technical Report, 2018–2025)},'' ARL-TR-10274 (JAN 2026), 1-120. 

\item
\textbf{Tschopp, M.A.}, Hobbs, R., Work, M., ``\href{https://doi.org/10.5281/zenodo.18443653}{Artificial Intelligence for Soldiers 2025: Enhancing AI Readiness for the Army},'' ARL-SR-0506 (JUN 2025), 1--79.

\item
\textbf{Tschopp, M.A.}, ``\href{https://doi.org/10.5281/zenodo.18443767}{Global Collaboration Dynamics in Scientific Research: Why Does It Occur? Examining the Citation Economy},'' ARL-TR-10058 (FEB 2025), 1--56.

\item
\textbf{Tschopp, M.A.}, ``\href{https://doi.org/10.5281/zenodo.18443725}{Global Collaboration Dynamics in Scientific Research: How Often Does It Occur},'' ARL-TR-10057 (FEB 2025), 1--72.

\item
\textbf{Tschopp, M.A.}, Hobbs, R., ``\href{https://doi.org/10.5281/zenodo.18443551}{Artificial Intelligence for Soldiers 2024: Experiences and Lessons Learned from the Inaugural Course},'' ARL-SR-0497 (JUL 2024), 1--112.

\item
\textbf{Tschopp, M.A.}, ``\href{https://apps.dtic.mil/sti/trecms/pdf/AD1222844.pdf}{From Scientific Institutions to Research Concepts to Global Collaboration and Beyond: Uncovering Patterns in Scientific Networks},'' ARL-SR-0493 (FEB 2024), 1--213.

\item
Hoppel, C., Stepp, D., Becker, R., Bakas, M., Vargas--Gonzalez, L., Tonge, A., \textbf{Tschopp, M.A.}, ``Controlling the Load Distribution in High-Strength Materials Army Science Planning and Strategy Meeting (ASPSM),'' ARL-SR-0438 (Feb 2021), 1--44.

\item
\textbf{Tschopp, M.A.}, {Joshi, K.}, Chowdhury, S., ``\href{https://apps.dtic.mil/dtic/tr/fulltext/u2/1059513.pdf}{Coupling Molecular Dynamics and Machine Learning for Predicting Aluminum Segregation to Magnesium Grain Boundaries},'' ARL-TR-8490 (Sep 2018), 1--40.

\item
Guziewski, M., Coleman, S.P., \textbf{Tschopp, M.A.}, ``\href{https://apps.dtic.mil/sti/pdfs/AD1047833.pdf}{Expansion and Automation of the Energy Conserving Orientational Force for Calculation of Grain Boundary Mobility},'' ARL-TR-8302 (Feb 2018), 1--42.

\item
{Khanzadeh, M.}, Chowdhury, S., Marufuzzaman, M., \textbf{Tschopp, M.A.}, Bian, L., ``\href{https://apps.dtic.mil/dtic/tr/fulltext/u2/1078016.pdf}{Using Self Organizing Maps for In-situ Monitoring of Melt Pool Thermal Profiles for Porosity Prediction in Laser-based Additive Manufacturing Processes},'' ARL-TN-0888 (June 2018), 1--31.

\item
\textbf{Tschopp, M.A.}, Hernandez, E.,  ``\href{https://apps.dtic.mil/sti/pdfs/AD1026967.pdf}{Quantifying Similarity and Distance Measures for Vector-based Datasets: Histograms, Signals, and Probability Distribution Functions},'' ARL-TN-0810, 1--40.

\item
\textbf{Tschopp, M.A.}, Nouranian, S., Baskes, M.I., Gwaltney, S.R., Horstemeyer, M.F., ``\href{https://apps.dtic.mil/sti/pdfs/AD1026964.pdf}{Influence of Parameters of a Reactive Interatomic Potential on the Properties of Saturated Hydrocarbons},'' ARL-TR-7850, 1--62.

\item
{Foley, D.}, Coleman, S.P.,  Tucker, G.J., \textbf{Tschopp, M.A.}, ``\href{https://apps.dtic.mil/sti/pdfs/AD1023687.pdf}{Voronoi-based Nanocrystalline Generation Algorithm for Atomistic Simulations},'' ARL-TN-0806, 1--44.

\item
\textbf{Tschopp, M.A.}, ``\href{https://apps.dtic.mil/sti/pdfs/AD1017883.pdf}{3-D Synthetic Microstructure Generation with Ellipsoid Particles},'' ARL-TN-0789, 1--32.

\item
{Foley, D.}, \textbf{Tschopp, M.A.}, Coleman, S.P., ``Nanocrystal Generation through Geometric Packing Algorithms,'' HIP-15-20 final report.

\item
\textbf{Tschopp, M.A.}, Maupin, H.E., ``\href{https://apps.dtic.mil/dtic/tr/fulltext/u2/a615166.pdf}{ARL Lightweight and Specialty Metals Branch Research and Development (FY14)},'' ARL-SR-0319, 1--64.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., Atwater, M.A., Kecskes, L.J., ``\href{https://apps.dtic.mil/sti/pdfs/ADA612940.pdf}{Low-Cost Structural Thermoelectric Materials: Processing and Consolidation},'' ARL-TR-7167, 1--28.

\item
\textbf{Tschopp, M.A.}, Darling, K.A.,  Atwater, M.A., ``\href{https://apps.dtic.mil/sti/pdfs/ADA612840.pdf}{Surpassing the Theoretical Limit of Porosity in Conventional Solid-State Foaming: Microstructure Characterization of Length Scales in a Copper Metal Foam},'' ARL-TR-7139, 1--60.

\item
\textbf{Tschopp, M.A.}, Darling, K.A.,  Atwater, M.A., Solanki, K.N., ``\href{https://apps.dtic.mil/dtic/tr/fulltext/u2/a611875.pdf}{Predicting Grain Growth in Nanocrystalline Materials: A Thermodynamic and Kinetic-Based Model Informed by High Temperature X-ray Diffraction Experiments},'' ARL-TR-7107, 1--79.

\item
\textbf{Tschopp, M.A.}, ``Atomistic Modeling Development for Nanocrystalline Metal Alloys,'' PETTT Final Technical Report, High Performance Computing Modernization Program, 2014.

\item
\textbf{Tschopp, M.A.}, Darling, K.A.,  Atwater, M.A., VanLeeuwen, B.K., Liu, Z.K., ``\href{https://apps.dtic.mil/dtic/tr/fulltext/u2/a590711.pdf}{Enhancing the High Temperature Capability of Nanocrystalline Alloys: Utilizing Thermodynamic Stability Maps to Mitigate Grain Growth Through Solute Selection},'' ARL-TR-6743, 1--53.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., ``Towards Predictive Models of Nanocrystalline Binary Metal Alloys: Role of Solutes and Interfaces on Segregation and Mechanics in Al-Based Nanocrystalline Systems (ISN Year 1 Report),'' ARL-SR-291.

\item 
\textbf{Tschopp, M.A.}, F. Gao, X. Sun,``Modeling of defect sinks at grain boundaries in Fe-Cr and Fe-He systems,'' U.S. Department of Energy, Nuclear Energy Advanced Modeling and Simulation, Fundamental Methods and Models Program, 2012 Quarterly Report.

\item 
\textbf{Tschopp, M.A.}, F. Gao, X. Sun,``\href{https://apps.dtic.mil/dtic/tr/fulltext/u2/1043117.pdf}{The Effects of the Uncertainty of Thermodynamic and Kinetic Properties on Nucleation and Evolution Kinetics of Cr-Rich Phase in Fe-Cr Alloys},'' U.S. Department of Energy, Nuclear Energy Advanced Modeling and Simulation Program, M3MS-12PN0606018, ARL-CR-0705, 1--52.

\item 
\textbf{Tschopp, M.A.}, ``\href{http://www.dtic.mil/docs/citations/ADA523928}{Damage Mechanics Model Development for Monocrystalline Superalloys},'' Defense Technical Information Center, ADA523928.

\item 
Fairchild, S., \textbf{Tschopp, M.A.}, Bartha, B.B., Murray, P.T., Porter, W.J., ``\href{http://www.dtic.mil/docs/citations/ADA502792}{Digital Image Correlation of Ni-base Superalloy Ren\'{e} 88DT Using \textit{In Situ} SEM Tension Experiments},'' Preprint, Defense Technical Information Center, ADA502792.

\item 
\textbf{Tschopp, M.A.}, Tiley, J.S., Viswanathan, G.B., ``\href{http://www.dtic.mil/docs/citations/ADA522026}{Automated Identification and Characterization of Secondary \& Tertiary gamma' Precipitates in Nickel-Based Superalloys},'' Preprint, Defense Technical Information Center, ADA522026.

\item
\textbf{Tschopp, M.A.}, Groeber, M.A., Simmons, J.P.,Rosenberger, A.H., Woodward, C., ``\href{http://www.dtic.mil/docs/citations/ADA546146}{Technique for Automated Extraction of Symmetric Microstructural Features: Application to Dendritic Cores in Single Crystal Ni-Based Superalloys},'' Preprint, Defense Technical Information Center, ADA546146.

\item 
Spowart, J.E., Wilks, G.B., \textbf{Tschopp, M.A.}, ``\href{http://www.dtic.mil/docs/citations/ADA501812}{Multi-Scale Characterization of Inhomogeneous Morphologically Textured Microstructures},'' Preprint, Defense Technical Information Center, ADA501812. 

\item 
\textbf{Tschopp, M.A.}, Wilks, G.B., Spowart, J.E., ``\href{http://www.dtic.mil/docs/citations/ADA489997}{Multi-Scale Characterization of Orthotropic Microstructures},'' Preprint, Defense Technical Information Center, ADA489997. 

\item 
\textbf{Tschopp, M.A.}, Wilks, G.B., Spowart, J.E., ``\href{http://www.dtic.mil/docs/citations/ADA523465}{Multiscale Characterization Technique for Chemically Reactive Multiphase Composite Microstructure},'' Preprint, Defense Technical Information Center, ADA523465. 

\item 
Groeber, M.A., Simmons, J., Rosenberger, A.H., Woodward, C., \textbf{Tschopp, M.A.},  Fahringer, R., ``\href{http://www.dtic.mil/docs/citations/ADA520551}{Symmetry-Based Automated Extraction of Microstructural Features: Application to Dendritic Cores in Single-Crystal Ni-Based Superalloys},'' Preprint, Defense Technical Information Center, ADA520551.

\item 
Bartha, B.B., John, R., Caton, M., Jha, S., Porter, W.J., Fairchild, S., Murray, T., \textbf{Tschopp, M.A.}, Li, K., Larsen, J.M., Szczepanski, C.J., Glavicic, M.G., Martin, P., ``\href{http://www.dtic.mil/docs/citations/ADA522042}{Modeling Complex Structural Geometry and Process Interaction},'' Defense Technical Information Center, ADA522042.

\item 
Tiley, J.S., Viswanathan, G.B., Shiveley, A., \textbf{Tschopp, M.A.}, Srinivasan, R., Fraser, H.L., Banerjee, R., ``\href{http://www.dtic.mil/docs/citations/ADA519441}{Measurement of gamma prime Precipitates in a Nickel-Based Superalloy using Energy-Filtered Transmission Electron Microscopy Coupled With Automated Segmenting Techniques},'' Preprint, Defense Technical Information Center, ADA519441.


\end{cvlist}
