\section{\sc Select Trade Journals \\ \& Popular \\ Press}

Name listed for authored articles in trade journals, press.  All other articles include quotes from me in an official capacity or highlights from regional engagement in ARL Central.

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item ``\href{https://www.army.mil/article/285626/army_scientists_train_soldiers_on_how_to_leverage_ai_technologies}{Army scientists train Soldiers on how to leverage AI technologies},'' ARL Public Affairs, 19 MAY 2025.
\begin{list2}
\item[$\star$] ``AI holds the extraordinary potential to swiftly analyze the deluge of data present within the future battlefield and to deliver actionable insight to Soldiers at the speed of relevance,'' Tschopp said. ``We want this course to equip Soldiers with the knowledge and decision-making capabilities to harness AI as a tool to gain a competitive edge over our adversaries.''
\end{list2}

\item ``\href{https://www.dvidshub.net/news/484157/operationalizing-science-jmc-with-artificial-intelligence-and-machine-learning}{Operationalizing Science at JMC with Artificial Intelligence and Machine Learning},'' Joint Munitions Command Public Affairs (OCT 2024).
\begin{list2}
\item[$\star$] ``AI and ML are not just buzzwords; they are powerful tools that are revolutionizing how we approach complex problems,'' said Tschopp. ``It’s essential that our Soldiers and Civilians understand not just the ‘what,' but also the ‘how' and ‘why' behind these algorithms. By demystifying these technologies, we are empowering our Soldiers and Civilians to leverage data-driven insights and make more informed decisions; ultimately, enhancing our operational capabilities.''
\end{list2}

\item ``\href{https://www.army.mil/article/246398/army_hosts_global_ai_machine_learning_event}{Army hosts global AI, machine learning event},'' ARL Press Release (MAY 2021).
\begin{list2}
\item[$\star$] ``A great demonstration of Army leadership in the field of machine learning, and an incredible job by Mark,'' said Gen. John M. Murray, [4-star] Commanding General (R) of the Army Futures Command. ``What started as a good idea, some initiative, and a desire to spread knowledge, was met with incredibly positive feedback. His short course showcased not only the challenges associated with building neural networks, but the Army's efforts to harness these capabilities.''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``\href{https://www.ndiaindiana.com/news/welcome-to-arl-central}{Welcome to ARL Central},'' National Defense Innovation Assocation and Indiana Innovation Institute (MAR 2021).
\begin{list2}
\item[$\star$] Authored an invited blog for NDIA--IN3 chapter of 600 members
\end{list2}

\item
``\href{https://www.army.mil/article/243587/army_argonne_scientists_explore_nanoparticles_for_future_weapon_systems}{Army, Argonne scientists explore nanoparticles for future weapon systems},'' ARL Press Release (FEB 2021).

\item
``\href{https://www.army.mil/article/240740/university_of_missouri_works_with_army_to_enhance_warfighter_technology}{University of Missouri works with Army to enhance warfighter technology},'' ARL Press Release (NOV 2020).

\item
``\href{https://www.army.mil/article/240059/army_adds_northwestern_engineers_to_team_finding_material_solutions}{Army adds Northwestern engineers to team finding material solutions},'' ARL Press Release (OCT 2020).

\item
``\href{https://www.army.mil/article/239661/army_readies_charging_port_for_autonomous_drone_swarms}{Army readies charging port for autonomous drone swarms},'' ARL Press Release (OCT 2020).

\item
``\href{https://www.army.mil/article/239529/army_unmanned_vehicles_to_get_hybrid_electric_power}{Army unmanned vehicles to get hybrid electric power},'' ARL Press Release (SEP 2020).

\item
``\href{https://www.army.mil/article/239240}{Army-funded research may enable drones to run on any type of fuel},'' ARL Press Release (SEP 2020).

\item
``\href{https://www.purdue.edu/newsroom/releases/2020/Q3/purdue,-u.s.-army-to-collaborate-on-next-generation-energetic-materials.html}{Purdue, U.S. Army to collaborate on next-generation energetic materials},'' Purdue Press Release (AUG 2020).

\item
``\href{https://thedaily.case.edu/u-s-army-commits-up-to-11-million-for-polymer-research/}{Case Western Reserve and Polymer Plus partner with Army research lab to develop manufacturing approaches for cost-effective production of lightweight, high-performance polymeric materials},'' CWRU Press Release (AUG 2020).

\item
``\href{https://www.youtube.com/watch?v=ZZYnXnp1FEw}{Army's Corporate Research Laboratory (ARL) Central: Video},'' Youtube (DEC 2019).

\item
``\href{https://computerscience.uchicago.edu/news/article/smart-cities-bases/}{UChicago Workshop Highlights Internet of Things Potential for Cities, Army Installations},'' U Chicago Press Release (JUL 2019).

\item
``{\href{https://www.army.mil/article/222975/army_focuses_on_power_propulsion_for_future_unmanned_aircraft_systems}{Army focuses on power, propulsion for future unmanned aircraft systems}},'' ARL Press Release (JUN 2019).

\item
``\href{https://www.army.mil/article/203716/army_researchers_conduct_first_ever_combustion_experiment_with_x_rays}{Army researchers conduct first-ever combustion experiment with X-rays},'' ARL Press Release (DEC 2018).

\item
``\href{https://www.army.mil/article/212535/army_lab_recognizes_scientific_contributions_of_postdocs_at_symposium}{Army lab recognizes scientific contributions of postdocs at symposium},'' ARL Press Release (OCT 2018).

\item
``\href{https://medium.com/invent2026/welcoming-army-research-lab-to-town-d29dd9c36ec5}{Welcoming Army Research Lab to town},'' Invent2026, Medium.com (OCT 2018).

\item
``\href{https://today.uic.edu/u-s-army-research-laboratory-taps-engineering-student-for-fellowship}{U.S. Army Research Laboratory taps engineering student for fellowship},'' UIC Press Release (OCT 2018).

\item
``\href{https://www.army.mil/article/199128/army_research_lab_selects_lead_for_new_regional_partnership}{Army Research Lab selects lead for new regional partnership},'' ARL Press Release (JAN 2018).

\item
``\href{https://www.army.mil/article/196840/arl_uchicago_forge_new_partnerships_in_the_greater_chicago_area}{ARL, UChicago forge new partnerships in the Greater Chicago Area},'' ARL Press Release (NOV 2017).

\item
``\href{https://www.army.mil/article/195649/us_army_research_laboratory_announces_new_partnership}{U.S. Army Research Laboratory announces new partnership},'' ARL Press Release (OCT 2017).

\item
``\href{https://www.army.mil/article/186569/army_materials_researcher_shares_passion_for_science_with_kids}{Army Researcher Makes Science Real for Elementary Students},'' Armed with Science (DoD) Press Release (MAY 2017), Army Press Release (APR 2017), RDECOM press release (APR 2017), ARL Press Release, APG News (APR 2017), British News Agency (MAY 2017).

\item
``\href{https://www.army.mil/article/189539/engineering_society_elects_army_researcher_as_fellow}{Engineering society elects Army researcher as fellow},'' RDECOM Press Release, Army Press Release, ARL Press Release (JUN 2017).

\item
``\href{https://www.army.mil/article/170983/scientific_society_honors_army_materials_researcher}{Scientific society honors Army materials researcher},'' ARL Press Release (JUL 2016).

\item
``\href{https://www.army.mil/article/164168/army_research_laboratory_wins_dod_grants_for_summer_interns}{Army Research Laboratory wins DOD grants for summer interns},'' ARL Press Release (MAR 2016).

\item
``\href{https://www.army.mil/article/151804/wearing_body_armor_strengthens_civilian_experience}{Wearing body armor strengthens civilian experience},'' ARL Press Release (JUL 2015).

\item
``\href{https://www.cavs.msstate.edu/story.php?d=387}{CAVS Studies High Temperature Aerospace Materials in Modern Turbine Engines},'' MSU CAVS press release (DEC 2013).

\item
\textbf{Tschopp, M.A.}, ``{Career Opportunities and Experiences in Materials Science and Engineering},'' ASM International Advanced Materials \& Processes (AUG 2013).

\item
\textbf{Tschopp, M.A.}, ``{MS\&T 2012 Symposium for Emerging Professionals: Early Strategies for Career Development},'' ASM International Advanced Materials \& Processes (AUG 2012).

\item
\textbf{Tschopp, M.A.}, ``{Integrated Computational Materials Engineering (ICME): A paradigm shift from materials selection to materials design},'' ASM International Advanced Materials \& Processes (MAR 2012).

\item
``CAVS studies radiation effects on nuclear reactor materials,'' MSU University Relations press release, Maroon Research magazine, 2012 Research Windows (MAR 2012).

\item
``\href{http://www.pnnl.gov/science/highlights/highlight.asp?id=1115}{Learning About Material Integrity from Statistical Data: Imaging, statistics, and computational analysis shed new light on defects},'' Pacific Northwest National Laboratory highlighted research (FEB 2012).

\end{cvlist}

