\section{\sc Invited Seminars}

Presenting Author in \textbf{Boldface} type

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Tschopp, M.A.}, ``Reflection of a Career: Careers in National Laboratories!,'' Case Western Reserve University, 17 SEP 2024.

\item
\textbf{Tschopp, M.A.}, ``Data is the New Bacon: Why Data is Sizzlin' Right Now,'' Army Management Staff College, Kickoff Invited Lecture for Data Foundations course, 14 JUN 2024.

\item
\textbf{Tschopp, M.A.}, Oie, K., ``Power Up Your Career: Come Learn about Sabbaticals,'' ARL Cafe Seminar, MAR 2024.

\item
\textbf{Tschopp, M.A.}, ``The Science of Science: How to Stand on the Shoulders of Giants (Without Falling Off),'' ARL Colloquium seminar, 14 FEB 2024 (120-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Star Wars $+$ Machine Learning $=$ Wait, what?! Exploring top mis-ML Concepts-ions,'' University of North Texas, 12 JAN 2024.

\item
\textbf{Tschopp, M.A.}, ``An Arsenal of Experiences: Maneuvering the Frontlines of a Modern PhD Career... to ARL,'' University of Chicago, 16 NOV 2023.

\item
\textbf{Tschopp, M.A.}, ``Star Wars and Machine Learning: Lessons Learned from the `somewhat familiar with ML' crowd,'' Carnegie Mellon University, 3 NOV 2023.

\item
\textbf{Tschopp, M.A.}, ``From Hallowed Halls to Army Strong: Navigating the World of Army-Academia Collaboration,'' Carnegie Mellon University, 3 NOV 2023.

\item
\textbf{Tschopp, M.A.}, ``How to do business with ARL,'' 2023 National Cybersecurity Education Colloquium (NCEC), Chicago, IL, 18--22 SEP 2023.
\begin{list2}
\item[$\star$] Invited panelist for ``Federal funding opportunities'' workshop, 22 SEP 2023, and
\item[$\star$] Invited member of invitation-only committee on ``Generative AI Tools and Cybersecurity'', 21 SEP 2023
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Adventures in Career-Shifting: Navigating the Unpredictable Roads of a Modern PhD Career... and... National Laboratories!,'' Case Western Reserve University, 19 SEP 2023.

\item
\textbf{Tschopp, M.A.}, ``Science of Science: Future Challenges and Opportunities,'' Columbia University, ARO Workshop on Decentralized Science, 17 AUG 2023.

\item
\textbf{Tschopp, M.A.}, ``Adventures in Career Shifting: Navigating the Unpredictable Roads of a Modern PhD Career,'' Northwestern University, 17 MAY 2023.

\item
\textbf{Tschopp, M.A.}, ``From Padawan to Jedi Master: Machine Learning with a Star Wars Twist,'' Northwestern University, Northwestern Institute on Complex Systems (NICO) Seminar Series, 10 MAY 2023.

\item
\textbf{Tschopp, M.A.}, ``The Sociology of Science: How to Stand on the Shoulders of Giants (Without Falling Off),'' Georgia Institute of Technology, ``Advances in Multiscale Mechanics and Materials Design'' symposium in honor of David McDowell's retirement, 14 APR 2023.

\item
\textbf{Tschopp, M.A.}, ``The Science of Science: How to Stand on the Shoulders of Giants (Without Falling Off),'' University of North Carolina--Chapel Hill, 4 APR 2023.

\item
\textbf{Tschopp, M.A.}, ``From Hallowed Halls to Army Strong: Navigating the World of Army-Academia Collaboration,'' University of North Carolina--Chapel Hill, 4 APR 2023.

\item
\textbf{Tschopp, M.A.}, ``Data is the New Bacon: Why Data is Sizzlin' Right Now,'' Army Management Staff College, Kickoff Invited Lecture for Data Foundations course.
\begin{list2}
\item[$\star$] 24 FEB 2023
\item[$\star$] 31 MAR 2023
\item[$\star$] 28 APR 2023
\item[$\star$] 23 JUN 2023
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``An ARL Perspective: Doing Business with the Army (Research Laboratory),'' Northwestern University, 9 NOV 2022.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory in Chicago? Tailored Ecosystem Engagement Model,'' SEN Baldwin National Security Advisor and Staff, 15 AUG 2022.

\item
\textbf{Tschopp, M.A.}, ``AI/ML in the DoD,'' 3rd Annual NDSEG Fellowship Conference, invited panel member, JUL 2022.

\item
\textbf{Tschopp, M.A.}, ``AI/ML in the Army and Air Force,'' Air Force MADLAB (Machines, Algorithms, Data Lab) Center of Excellence Workshop, invited panel member, JUN 2022.

\item
\textbf{Tschopp, M.A.}, ``The National Laboratory Career Path,'' (virtual) Georgia Tech Teaching Practicum, 28 SEP 2021.

\item
\textbf{Tschopp, M.A.}, ``AI/ML for Materials Design: Steels,'' (virtual) DoD Steels Conference, invited panel member, OCT 2021.

\item
\textbf{Tschopp, M.A.}, ``Tri-Service Panel on Careers in the DoD,'' 2nd Annual NDSEG Fellowship Conference, invited panel member, 19--21 JUL 2021.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory: big Army to AFC to ARL,'' (virtual) ARL--Georgia Tech Workshop on Materials $+$ Manufacturing Science and Engineering, plenary talk, 26 MAY 2021.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory: A Short Introduction to the Corporate R\&D Laboratory for the Army,'' (virtual) ARL--Georgia Tech Workshop on Materials $+$ Manufacturing Science and Engineering, plenary talk, 25 MAY 2021.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' (virtual) University of Chicago Center for Decision Research, APR 2021.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Washington University at St Louis, 11 JAN 2021.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory---Computational \& Information Science Research,'' University of Illinois--Chicago, Computer Science seminar, 23 OCT 2020.
\begin{list2}
\item[$\star$] Split seminar with 2 ARL scientists: Dr.~Celso de Melo, Dr.~Mark Dennison
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network: Mission, People, Open Campus,'' Midwest Defense Innovation Summit, invited panel member, 21 OCT 2020.
\begin{list2}
\item[$\star$] ``On behalf of the organizing committee of the Midwest Defense Innovation Summit, we would like to extend a sincere thank you for your participation in this inaugural event. We have been overwhelmed by positive feedback from attendees and we have you to thank for that,'' Midwest Defense Innovation Summit Organizing Committee.
\item[$\star$] Other panel members: AFRL Director, ONR Global Director
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory -- Advanced Electronics and Electronic Warfare,'' University of Illinois--Chicago, Electrical and Computer Engineering department seminar, 16 OCT 2020.
\begin{list2}
\item[$\star$] Split seminar with 2 ARL scientists: Dr.~Romeo del Rosario, Dr.~Neil Vallestero
\item[$\star$] ``Thank you for all your efforts in organizing a great set of talks for us today. I think all of you generated a great deal of excitement and there will be many emails to you about possible collaborations. As you could tell there were a few faculty who were there who were just interested in finding out about funding but many of the others were interested in engaging and collaborating and students who were present particularly those in ECE stayed on for a while and Neil and Romeo were very kind to answer their questions.''  Mitra Dutta, former VCR, UIC.
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory -- BioEngineering Research in ARL?,'' University of Illinois--Chicago, Bioengineering department seminar, 16 OCT 2020.
\begin{list2}
\item[$\star$] Split seminar with 2 ARL scientists: Ms. Ashley Eidsmore, Dr.~Carolyn Hampton 
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central -- Disrupting Defense S\&T for Future Capabilities,'' University of Colorado--Boulder, 14 OCT 2020.
\begin{list2}
\item[$\star$] ``From our perspective, it was excellent. Overall, excellent event thought from my end...  thanks to you, Bill and Catie for putting together.'' Massimo Ruzzene, Associate Dean for Research
\item[$\star$] Organized faculty research webinar with CU-Boulder Office of Research
\item[$\star$] 15 ARL Scientists in 5 follow-on Technical Breakout Sessions
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``ARL Central, Polycrystalline Materials by Design, and other Short Stories,'' University of Illinois--Chicago, Civil and Materials Engineering department seminar, 9 OCT 2020.

\item
\textbf{Tschopp, M.A.}, ``Early Career Panel Discussion -- Career Development,'' TechEvent -- 2020 Postdoc and Early Career Symposium, invited panel member, 16 SEP 2020.

\item
\textbf{Tschopp, M.A.}, ``AAMP-UP! Career Path, Career Development, Army Research Laboratory and Army Science \& Technology,'' Purdue University AAMP-UP career seminar, JUN 2020.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Ohio State University, DEC 2019.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Iowa State University, NOV 2019.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Colorado University--Boulder, NOV 2019.

\item
\textbf{Tschopp, M.A.}, ``Wait... What? The Army has a Corporate Research Laboratory?!?!'' Colorado State University, NOV 2019.

\item
\textbf{Tschopp, M.A.}, ``ARL Central, Polycrystalline Materials by Design, and other Short Stories,'' Colorado School of Mines, NOV 2019.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory Network? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Colorado School of Mines, NOV 2019.

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory in Midwest? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Argonne National Laboratory, OCT 2019.

\item
\textbf{Tschopp, M.A.}, ``ARL Central, Polycrystalline Materials by Design, and other Short Stories,'' University of Wisconsin--Madison, Lindbergh Lecture Seminar Series, 19 SEP 2019  (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory in Wisconsin? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' University of Wisconsin--Madison, Faculty Lunchtime Lecture, 19 SEP 2019 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Research and Technology for Operating Environments of the Future, i.e., `Cool Stuff that We are Working On','' 425 9$^{th}$--12$^{th}$ grade students, Peoria Public School District, 6 SEP 2019 (educating students about STEM, STEM careers in the Army, and the Army Research Laboratory).

\item
\textbf{Tschopp, M.A.}, ``ARL-Central: JeopARLdy \& the informal (Pizza) Lunch 'N Learn,'' Northwestern University, 16 AUG 2019 (75 minute seminar/discussion/Jeopardy Quiz Show).

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory in Indiana? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' Indiana University--Bloomington, JUL 2019 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory in Chicago? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,''  Illinois Institute of Technology, 29 MAY 2019  (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Army Research Laboratory at U Minnesota? The Army's Open Campus Business Model and ARL Central--Disrupting Defense S\&T for Future Capabilities,'' University of Minnesota, 13 MAY 2019 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``KEYNOTE: Army Research Laboratory and the Army's Open Campus Initiative:~Disrupting Defense S\&T for Future Capabilities,'' Chicago State Center for Intelligence and Security Research (CINSER), 18 APR 2019.

\item
\textbf{Tschopp, M.A.}, ``The Army Research Laboratory, The Army Research Laboratory Central, and NSWC--Crane I," NSWC--Crane Leadership, Merrillville, IN, 17 APR 2019 (120-minute seminar/questions).

\item
\textbf{Tschopp, M.A.}, ``The Army Futures Command, The Army Research Laboratory, The Army Research Office, The Army Research Laboratory Central, Notre Dame, and You (A$^4$ND You),'' Notre Dame University, 6 MAR 2019 (30-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL-Central: An `Open' Extended Model for Defense S\&T,'' Notre Dame, 27 FEB 2019 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL Central Roadshow: Past, Present, and Future,'' Army Research Laboratory 12 DEC 2018, 13 DEC 2018, 9 JAN 2019, 13 FEB 2019 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Application of Machine Learning in Materials Science,'' University of Illinois--Chicago, 31 OCT 2018 (60-minute seminar/discussion).

\item
\textbf{Tschopp, M.A.}, ``ARL Central, Polycrystalline Materials by Design, and other Short Stories,'' Purdue University, MSE Seminar Series, 26 OCT 2018  (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL-Central: An `Open' Extended Model for Defense S\&T,'' University of Illinois--Urbana-Champaign, 25 OCT 2018 (30-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL-Central: An `Open' Extended Model for Defense S\&T,'' University of Wisconsin--Madison, 24 OCT 2018 (30-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL-Central: An `Open' Extended Model for Defense S\&T,'' (made to representatives from all Milwaukee universities), University of Wisconsin--Milwaukee, 10 SEP 2018  (invited 60-minute seminar--90 minutes with questions).

\item
\textbf{Tschopp, M.A.}, Tracy V.~Shephard (WMRD-LD DC), ``ARL at U Chicago? An `Open' Extended Model for Defense S\&T -- ARL Central,'' University of Chicago Chemistry Department,  7 SEP 2018  (invited 60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL-Central: An `Open' Extended Model for Defense S\&T,'' Northern Illinois University, 9 AUG 2018  (invited 60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``ARL in Chicago?  Nucleation and Growth of an `Open' Extended Model for Defense S\&T -- ARL Central,'' ASM Materials Professional Society, Chicago, IL, 20 MAR 2018 (invited 60-minute keynote).

\item
\textbf{Tschopp, M.A.}, ``ARL in the Midwest?  An `Open' Extended Model for Defense S\&T -- ARL Central,'' Marquette University, 8 MAR 2018  (invited 60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Polycrystalline Materials by Design at Army Research Laboratory,'' Center for Hierarchical Materials Design (ChiMaD), Northwestern University, 6 DEC 2017 (invited 60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Materials by Design of Polycrystalline Materials at the US Army Research Laboratory,'' University of Connecticut, 8 SEP 2017 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Materials Engineering,'' 4$^{th}$ grade class, Homestead Wakefield Elementary School, 2 JUN 2017 (2 60-minute talks).

\item
\textbf{Tschopp, M.A.}, ``Materials by Design of Polycrystalline Materials,'' Mississippi State University, 2017 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Materials by Design of Polycrystalline Materials,'' Georgia Tech, 2017 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Materials Engineering,'' 4$^{th}$ grade class, Homestead Wakefield Elementary School, 7 APR 2017 (75-minute talk).

\item
\textbf{Tschopp, M.A.}, ``Integrated Computational Materials Engineering: Accelerating Materials Discovery, Development, and Design by Merging Mechanical Engineering, Materials Science, and Computational Science,'' ARL Colloquia and Science Caf\'{e}, 22 FEB 2017 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Polycrystalline Materials by Design,'' UT-Arlington, 3 FEB 2017 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Polycrystalline Materials by Design,'' Texas A\&M, 1 FEB 2017 (60-minute seminar).

\item
\textbf{Tschopp, M.A.}, ``Understanding Structure-Property Relationships of Grain Boundaries and Interfaces for Materials Design,'' Johns Hopkins University, 16 SEP 2016, Baltimore, MD.
\begin{list2}
\item[$\star$] HEMI invited seminar, associated with MEDE CRA
\end{list2}

\item
\textbf{Tschopp, M.A.}, \textbf{Hernandez, E.}, ``Army Research Laboratory Organization, Mission, and Research:~Combining Design with Materials Science for Next Generation Material Development,'' University of Buffalo, 11 AUG 2016, Buffalo, NY.

\item
\textbf{Tschopp, M.A.}, \textbf{Coleman, S.P.}, ``Materials by Design at Army Research Laboratory,'' NASA-Langley, 1 AUG 2016, Hampton, VA.

\item
\textbf{Tschopp, M.A.}, \textbf{Holmes, L.J.}, ``ARL and Additive Manufacturing Overview'', U.S.~National Committee on Theoretical and Applied Mechanics, 22 APR 2016, The National Academies Building, Washington, DC.
\begin{list2}
\item[$\star$] Highlighted on ARL Public Affairs, ``Researchers invited to speak about ARL and Additive Manufacturing at U.S. National Committee on Theoretical and Applied Mechanics''
\item[$\star$] 1 of 8 invited speakers for this panel of experts in Theoretical and Applied Mechanics, which included the NAE president (National Academy of Engineering) Dr.~Dan Mote, the Director of ERDC Dr.~Jeffery Holland, the Chief Scientist of DHS Dr.~Kevin Brown, et al.
\item[$\star$] Kudos email, Wing Kam Liu, PhD, PE, President of the International Association for Computational Mechanics, Chair of the US National Committee on Theoretical and Applied Mechanics, ``On behalf of the US National Committee on Theoretical and Applied Mechanics, we thank you very much for taking your valuable time to come visit and talk to us. Our Members and other researchers, including those watching/listening via WebEx, appreciated very much your presence and the enlightening lectures.''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Understanding and Exploiting Structure-Property Relationships of Interfaces for Materials Design,'' University of Cincinnati, 4 MAR 2016, Cincinnati, OH.

\item
\textbf{Tschopp, M.A.}, ``U.S.~Army Research Laboratory:~An Intro to our Organization and Materials Research,'' Mississippi State University, 6 JAN 2016, Starkville, MS.

\item
\textbf{Tschopp, M.A.}, ``ARL Grain Boundary Science and Engineering,'' Carnegie Mellon University, 20 OCT 2015, Pittsburgh, PA.
\begin{list2}
\item[$\star$] Led visit with 9 ARL S\&Es, mostly early career to spark ideas and collaboration
\item[$\star$] Led to recruitment of PhD student Dr.~Philip Goins, now ARL Staff Scientist
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Engineering Nanoscale Interfaces for Metals Design,'' National Institute for Standards and Technology (NIST), 26 AUG 2015, Gaithersburg, MD.

\item
\textbf{Tschopp, M.A.}, ``Armed with Science: Career Experiences and Opportunities within Government Defense Laboratories,'' University of Michigan, College of Engineering Postdoctoral Association, 13 JUL 2015, Ann Arbor, MI.
\begin{list2}
\item[$\star$] Kudos letter from Elizabeth Wagner, College of Engineering, Office of the Dean of Research, University of Michigan, ``On behalf of the College of Engineering Postdoc Advisory Group, I would like to express our deep appreciation for your recent outreach to the College of Engineering student and postdoctoral research fellow communities. You were the first speaker for our new postdoc programming, and it was terrific launch. Your July 13th seminar, Armed with Science: Career Experiences and Opportunities within Government Defense Laboratories, provided a well-rounded overview of the career options available for doctoral students and postdocs, and highlighted the pros and cons of working in a government defense lab. Since your talk, several postdocs have let me know that your talk introduced them to the array of available research opportunities and created an interest in exploring career opportunities in a national laboratory.''
\item[$\star$] Led to recruitment of PhD student Dr.~Efrain Hernandez, now ARL Staff Scientist
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Understanding and Exploiting Structure-Property Relationships of Interfaces for Metallurgical Design,'' Northeastern University, 1 MAY 2015, Boston, MA.

\item
\textbf{Tschopp, M.A.}, ``A fresh take on... Engineering Interfaces at the Nanoscale for Metallurgical Design,'' Stony Brook University, 1 APR 2015, Stony Brook, NY.

\item
\textbf{Tschopp, M.A.}, ``In the Army Now: Career Experiences and Opportunities in Government Defense Laboratories,'' Missouri University of Science and Technology, 13 FEB 2015, Rolla, MO.

\item
{\textbf{Coleman, S.P.}}, \textbf{Tschopp, M.A.}, ``Virtual Diffraction: Linking Simulation and Experiment,'' Missouri University of Science and Technology, FEB 13, 2015, Rolla, MO.

\item
\textbf{Tschopp, M.A.}, ``The ABCs of ICME and other cool stuff,'' Missouri University of Science and Technology, 12 FEB 2015, Rolla, MO.
\begin{list2}
\item[$\star$] Kudos letter from Dr.~Wayne Huebner, department chair, Missouri University of S\&T: ``Your visit and presentation on February 12th could be used as a poster child of what an alum can do to inspire students. Great job! Your presentation was the perfect blend of science, engineering \& humor. Your ability to take a deep subject matter and make it understandable to everyone in the audience was remarkable. I know that the students walked away thinking about how ICME will be used as a tool to shape the future."
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Overview of Recent Materials Research in WMRD/LSMB and Opportunities/Interest for Expanding Materials-by-Design Capability,'' ARL-CISD Seminar, 14 JAN 2015.

\item
{\textbf{Coleman, S.P.}}, \textbf{Tschopp, M.A.}, ``Virtual Diffraction in Atomistic Simulations,'' ARL-CISD Seminar, JAN 14, 2015.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., Kecskes, L., Murdoch, H.A., ``The ``Nanocrystalline Metals'' Renaissance of the 21st Century: Tailoring ``Bulk'' Nanocrystalline Metals for Enhanced Thermal Stability and Mechanical Properties,'' Arizona State University, 12 SEP 2014.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., Kecskes, L., Murdoch, H.A., ``\href{http://dx.doi.org/10.13140/2.1.1582.6726}{The ``Nanocrystalline Metals'' Renaissance of the 21st Century: Tailoring ``Bulk'' Nanocrystalline Metals for Enhanced Thermal Stability and Mechanical Properties},'' Los Alamos National Laboratory, 8 SEP 2014.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., Kecskes, L., Murdoch, H.A.,  ``A New Beginning for ``Bulk'' Nanocrystalline Metals: Tailoring the Composition, Processing, and Structure for Enhanced Thermal Stability and Mechanical Properties of Nanocrystalline Metals,'' Mississippi State University, 19 MAY 2014.

\item
\textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.13140/2.1.5154.3847}{Twinning in HCP metals: Everyday I'm Shuffling},'' California Institute of Technology, 15 NOV 2013, Solid Mechanics Seminar, Pasadena, CA.

\item
\textbf{Tschopp, M.A.}, ``\href{http://dx.doi.org/10.13140/2.1.3417.6808}{Bridging the Gap between Solid Mechanics and Materials Science: Integrating Critical Experiments and Simulations for Computational Multiscale Modeling},'' University of Alabama, 15 APR 2013, Tuscaloosa, AL.
\begin{list2}
\item[$\star$] Faculty position interview, Materials Science and Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Bridging the Gap between Solid Mechanics and Materials Science: Integrating Critical Experiments and Simulations for Computational Multiscale Modeling,'' Florida International University, 7 MAR 2013, Miami, FL.
\begin{list2}
\item[$\star$] Faculty position interview, Mechanical and Materials Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Bridging the Gap between Solid Mechanics and Materials Science: Integrating Critical Experiments and Simulations for Computational Multiscale Modeling,'' Johns Hopkins University, 7 DEC 2012, Baltimore, MD.

\item
\textbf{Tschopp, M.A.}, ``Bridging the Gap between Solid Mechanics and Materials Science: Integrating Critical Experiments and Simulations for Computational Multiscale Modeling,'' Army Research Laboratory, WMRD, Ceramics and Transparent Armor Branch, 28 SEP 2012, Aberdeen, MD.

\item
\textbf{Tschopp, M.A.}, ``Bridging the Gap between Solid Mechanics and Materials Science: Integrating Critical Experiments and Simulations for Computational Multiscale Modeling of Metals,'' Army Research Laboratory, 12 JUL 2012, Aberdeen, MD.

\item
\textbf{Tschopp, M.A.}, ``Exploring the nanoscale mechanisms of dislocation and twin nucleation in fcc and hcp polycrystalline materials,'' Seminar, University of North Texas, 4 APR 2012, Denton, TX.
\begin{list2}
\item[$\star$] Faculty position interview, Mechanical Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Exploring the nanoscale mechanisms of dislocation and twin nucleation in fcc and hcp polycrystalline materials,'' Seminar, Brown University, 8 MAR 2012, Providence, RI.
\begin{list2}
\item[$\star$] Faculty position interview, Mechanical Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Transforming the Paradigm for Future Materials Design: Materials Innovation and Infrastructure Development for ICME and the Materials Genome Initiative,'' Seminar, University of Florida, 13 FEB 2012, Gainesville, FL.
\begin{list2}
\item[$\star$] Faculty position interview, Materials Science and Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Material Innovation and Infrastructure Development for Material Applications in Wind Energy,'' Seminar, University of Iowa, 6 FEB 2012, Iowa City, IA.
\begin{list2}
\item[$\star$] Faculty position interview, Mechanical Engineering department (Wind Energy thrust)
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Quantifying Material Structure-Property Relationships and Uncertainties at the Nanoscale for Computational Design of Material Systems,'' Seminar, Lawrence Livermore National Laboratory, 2 FEB 2012, Livermore, CA.

\item
\textbf{Tschopp, M.A.}, ``Quantifying Material Structure-Property Relationships and Uncertainties at the Nanoscale for Computational Design of Material Systems,'' Seminar, Sandia National Laboratory, 1 FEB 2012, Livermore, CA.

\item
\textbf{Tschopp, M.A.}, ``Quantifying Material Structure-Property Relationships and Uncertainties at the Nanoscale for Computational Design of Material Systems,'' Seminar, Pacific Northwest National Laboratory, 31 JAN 2012, Richland, WA.

\item
\textbf{Tschopp, M.A.}, ``Quantifying Structure-Property Relationships for Computational Materials Design: Applicability to Aerospace Engineering,'' Seminar, Mississippi State University, 16 NOV 2011, Starkville, MS.
\begin{list2}
\item[$\star$] Faculty position interview, Aerospace Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Quantifying Structure-Property Relationships for Computational Materials Design: Applicability to Automotive Engineering,'' Seminar, Clemson University (ICAR), 27 JUL 2011, Greenville, SC.
\begin{list2}
\item[$\star$] Faculty position interview, Automotive Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.} ``Towards Developing Automated Digital Image Processing Techniques: Application to Microstructure Characterization and Feature Extraction,'' Seminar, Mississippi State University (CAVS), MAY 2011, Starkville, MS.

\item
\textbf{Tschopp, M.A.}, ``MEAM Interatomic Potential Generation: Coupling MATLAB with Atomistic Codes,'' 3rd Annual NIST Workshop on Atomistic Simulations for Industrial Needs, 27--28 JUL 2010, Gaithersburg, MD.

\item
\textbf{Tschopp, M.A.}, ``Structure-property relationships at the atomistic scale,'' Seminar, University of Michigan, JUL 2010, Ann Arbor, MI.

\item
\textbf{Tschopp, M.A.}, ``Structure-property relationships at the atomistic scale: Applications to metals and polymers,'' Seminar, Pacific Northwest National Laboratory, 26 APR 2010, Richland, WA. 

\item
\textbf{Tschopp, M.A.}, ``Structure-property relationships at the atomistic scale: Applications to metals and polymers,'' Seminar, Washington State University, 28 APR 2010, Pullman, WA.

\item
\textbf{Tschopp, M.A.}, ``Integrated Computational Materials Engineering Research: Atomistic Structure-Property Relationships \& Microstructure Sensitive Design,'' Seminar, Texas A\&M, 13 MAY 2009, College Station, TX.
\begin{list2}
\item[$\star$] Faculty position interview, Mechanical Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Integrated Computational Materials Engineering Research: Atomistic Structure-Property Relationships \& Microstructure Sensitive Design,'' Seminar, Drexel University, 20 APR 2009, Philadelphia, PA.
\begin{list2}
\item[$\star$] Faculty position interview, Mechanical Engineering department
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Integrated Computational Materials Engineering Research: Atomistic Structure-Property Relationships \& Microstructure Sensitive Design,'' Seminar, Mississippi State University, 1 APR 2009, Starkville, MS.
\begin{list2}
\item[$\star$] Faculty position interview, Center for Advanced Vehicular Systems
\end{list2}

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Dislocation nucleation in $\Sigma3$ asymmetric tilt grain boundaries,'' Seminar, Georgia Tech, 15 FEB 2007, Atlanta, GA.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Atomistic Modeling of Grain Boundary Structure and Dislocation Nucleation,'' Seminar, Air Force Research Lab (AFRL) Materials Directorate, 23 OCT 2006, WPAFB, OH.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Microrotation-Augmented Energy-Minimization for Generating Nanocrystalline Cu Structures,''  Seminar, Georgia Institute of Technology, 28 OCT 2005, Atlanta, GA.

\item
\textbf{Tschopp, M.A.}, Spearot, D.E., McDowell, D.L., ``Dislocation or Disclination? Comparison of Theory and Observations,''  Seminar, Georgia Institute of Technology, 25 FEB 2005, Atlanta, GA.

\end{cvlist}

\section{\sc Invited Conference Presentations}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Tschopp, M.A.}, ``Science of Science. Standing on the Shoulders of Giants (Without Falling Off): Navigating the World of Scientific Knowledge,'' NDSEG 2023 Conference, 30 JULY 2023 (invited 60-minute talk).

\item
\textbf{Shawn Coleman}, Daniel Foley, Garritt Tucker, {Tschopp, M.A.}, ``Nanocrystalline Cu Deformation Characterization Simulations,''  TMS 2018, MAR 14, 2018 (invited 30-minute talk).

\item
\textbf{Tschopp, M.A.}, ``Using data science and data analytics to understand and quantify structure-property relationships in materials,'' International Conference on Plasticity, Damage, and Fracture, 7 JAN 2018 (invited 30-minute talk).

\item
\textbf{Tschopp, M.A.}, ``SAUQIPAM: Sensitivity Analysis and Uncertainty Quantification of Interatomic Potentials for Atomistic Modeling,'' MRS 2017 Conference, 28 NOV 2017 (invited 30-minute talk).

\item
\textbf{Tschopp, M.A.}, ``'Would you say I have a Plethora of Grain Boundaries?' An Interfacial Property Data Repository for Generating, Storing, Curating, and Using Grain Boundaries,'' Society of Engineering Science, 27 JUL 2017 (invited 40-minute talk).

\item
\textbf{Tschopp, M.A.}, ``Quantifying Uncertainty from (Pseudo)potentials for First Principles and Classical Atomistic Potentials,'' TMS 2017, 27 FEB 2017  (30-minute invited talk).

\item
\textbf{Tschopp, M.A.}, ``Quantifying Structure-Property Relationships of Grain Boundaries and Interfaces at the Atomic Scale for Design of Polycrystalline Materials,'' TMS 2017, 27 FEB 2017 (20-minute invited talk).

\item
Shawn Coleman, \textbf{Efra\'in Hern\'andez--Rivera}, DeCarlos Taylor, Jenn Synowczynski-Dunn, Mark A. Tschopp, ``Validation and optimization of boron carbide interatomic potentials using XRD,'' International Conference \& Exposition on Advanced Ceramics \& Composites, JAN 2017, Daytona Beach, FL (30-minute invited talk).

\item
\textbf{Tschopp, M.A.}, ``Influence of Grain Boundary Structure on Segregation of Point Defects, Helium, and Hydrogen,'' ASME IMECE 2016, 16 NOV 2016 (40-minute invited talk).

\item
\textbf{Tschopp, M.A.}, ``Multiscale Approach to Engineering Microstructure in Boron-Based Armor Ceramics,'' ASME IMECE 2016, 14 NOV 2016 (40-minute invited talk).

\item
\textbf{Tschopp, M.A.}, Hernandez, E., Coleman, S, Chowdhury, S., ``A Metamodeling Approach for Parameter Sensitivity Analysis and Uncertainty Quantification in a Boron-Carbide Interatomic Potential,'' MS\&T 2016, 26 OCT 2016 (40-minute invited talk).

\item
Daniel Foley, Shawn Coleman, \textbf{Garritt Tucker}, Mark Tschopp,  ``Linking Nanoscale Deformation Mechanisms and Interfaces with Diffraction Profiles in Nanocrystalline Materials,'' MS\&T 2016, OCT 24, 2016 (40-minute invited talk).

\item
\textbf{Tschopp, M.A.}, ``Microstructure as Data: Microstructure Quantification and Analysis for Materials Design,'' MS\&T 2016, 24 OCT 2016 (40-minute keynote).

\item
\textbf{Tschopp, M.A.}, ``Understanding and Exploiting Structure-Property Relationships of Grain Boundaries and Interfaces for Materials Design,'' Society of Engineering Science, 2 OCT 2016 (invited talk).

\item
\textbf{Tschopp, M.A.}, ``Integrated Computational Materials Engineering: Accelerating Materials Discovery, Development, and Design by Merging Mechanical Engineering, Materials Science, and Computational Science,'' all-invited talk `Short Course on ICME' symposium, 2015 ASME IMECE Annual Conference, Houston, TX.

\item
\textbf{Tschopp, M.A.}, Waas, T., Spadaccini, C., Madison, J., Arnold, S., ``Integrated Computational Materials Engineering,'' `Short Course on ICME' panel, 2015 ASME IMECE Annual Conference, Houston, TX (invited panel speaker).

\item
\textbf{Tschopp, M.A.}, ``I got my degree. What now?,'' MS\&T 2015, 7 OCT 2015, Columbus, OH (invited panel speaker).

\item
\textbf{Tschopp, M.A.}, Coleman, S.P., Synowczynski-Dunn, J., ``Engineering Interfaces at the Nanoscale for Polycrystalline Design,'' MS\&T 2015, 7 OCT 2015, Columbus, OH.

\item
\textbf{Darling, K.A.}, Roberts, A.J., \textbf{Tschopp, M.A.}, Hornbuckle, B.C., Kecskes, L.J., ``Developing Stable Bulk Nanocrystalline Cu Alloys from Powder Precursors,'' International Workshop on Interfaces at Bear Creek, SEP 30, 2015, Bear Creek, PA.

\item
\textbf{Tschopp, M.A.}, ``Microstructure Quantification and Analysis for ICME of High Temperature Alloys,'' TMS 2015, High-Performance Aerospace Alloys Design Using ICME Approach symposium, 17 MAR 2015, Lake Buena Vista, FL.

\item
\textbf{Darling, K.A.}, \textbf{Tschopp, M.A.}, Kecskes, L.J., ``Effect of Processing Parameters on the Microstructure of Mechanically Alloyed Nanostructured Al--Mn Alloys,'' TMS 2015, Advanced Composites for Aerospace, Marine, and Land Applications II symposium, MAR 16, 2015, Lake Buena Vista, FL.

\item
\textbf{Tschopp, M.A.}, ``Armed with Science: Career Experiences and Opportunities in Government Defense Laboratories,'' MS\&T 2014, Perspectives for Emerging Materials Professionals -- Career Perspectives for Emerging Materials Professionals symposium, 14 OCT 2014, Pittsburgh, PA.

\item
\textbf{Gao, F.}, Yang, L, Gao, N., {Tschopp, M.A.}, Kurtz, R.J., ``Evolution of Nano Gas bubbles: Atomistic Simulations at Experimental Time Scales,'' CAARI 2014, International Conference on the Application of Accelerators in Research and Industry, MAY 25--30, 2014, San Antonio, TX.

\item
\textbf{Tschopp, M.A.}, El Kadiri, H., Barrett, C.D.,  ``Towards understanding shear and shuffles during compound twinning in hexagonal close-packed structures (Everyday I'm Shuffling!),'' TMS 2014, 16--20 FEB 2014, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Nouranian, S.,  ``\href{http://dx.doi.org/10.13140/2.1.1844.8165}{Understanding and Automating the Design Aspects of Interatomic Potential Design (Being Mike Baskes: Cloning Mike's Brain for the Future of Interatomic Potential Design)},'' TMS 2014, 16--20 FEB 2014, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Atwater, M.A., Darling, K.A., ``\href{http://dx.doi.org/10.13140/2.1.2893.3921}{\textit{Expanding} solid-state foaming: Intraparticle expansion as a means to enhance porosity in metals},''  TMS 2014, 16--20 FEB 2014, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., Kecskes, L., Roberts, A.J., Kapoor, D., Mathaudhu, S., Zahrah, T., ``Bulk Consolidation of Nanostructured Cu-Ta Alloys,''  TMS 2014, 16--20 FEB 2014, San Diego, CA.

\item
\textbf{Nouranian, S.}, {Tschopp, M.A.}, Gwaltney, S.R., Baskes, M.I.,  Horstemeyer, M.F., ``A Parameterized Interatomic Potential for Saturated Hydrocarbons Using the Modified Embedded-Atom Method,'' TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Kecskes, L., Darling, K.A., ``High Strain Rate Properties of Nanostructured Cu-Ta Alloys,'' TMS 2014, 16--20 FEB 2014, San Diego, CA.

\item
\textbf{Bhattia, M.A.}, Adlakha, I., Solanki, K.N., {Tschopp, M.A.}, ``Energetically-driven approach for evaluating hydrogen enhanced localized plasticity versus hydrogen enhanced decohesion mechanisms in iron,'' TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Gao, F.}, Yang, L., Heinisch, H., Jiang, W., Kurtz, R.J., Terentyev, D., He, X.F., {Tschopp, M.A.}, ``Modeling He Effects on Microstructure Evolution in $\alpha$-Fe,'' 16th International Conference on Fusion Reactor Materials, Beijing, China, OCT 20--26, 2013.

\item
\textbf{Tschopp, M.A.}, ``Characterizing Primary Dendritic Microstructures to Quantify the Processing-Structure-Property Relationship In Single Crystal Nickel-Based Superalloys,'' ASME 2013 IMECE, 19 NOV 2013, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Darling, K.A., Kecskes, L., Murdoch, H.A.,  ``Grain Boundaries Galore: Tailoring the Composition, Processing, and Structure for Enhanced Thermal Stability and Mechanical Properties of Nanocrystalline Metals,'' MS\&T 2013, 27--31 OCT 2013, Montreal, Canada.

\item
\textbf{Tschopp, M.A.}, Gao, F., Solanki, K.N., Sun, X., ``Energetics and length scales of point defect and element segregation to grain boundaries in Fe,'' TMS 2013, Modeling and Experimental Validation of Multiscale Mechanical Behavior from Atomic Scale to Macro Scale symposium, 7 MAR 2013, San Antonio, TX.

\item
\textbf{Tschopp, M.A.}, Atwater, M.A., Hammond, V.H., Roberts, A.J., Maupin, H.E., Darling, K.A., Kecskes, L.J., ``Influence of Processing Parameters on the Microstructure and Mechanical Properties of Lightweight High Entropy Alloys,'' TMS 2013, Symposium on High Entropy Alloys, 7 MAR 2013, San Antonio, TX.

\item
\textbf{Gao, F.}, {Tschopp, M.A.}, Yang, L., Hu, S., Heinisch, H., Kurtz, R., ``Multiscale Modeling of He Effects on Microstructure Evolution in Alpha-Fe,'' TMS 2013, Mesoscale Computational Materials Science of Energy Materials: Irradiation and Defects symposium, MAR 5th, 2013, San Antonio, TX.

\item
\textbf{Gao, F.}, Yang, L., Li, Y., Hu, S., Sun, X., {Tschopp, M.A.}, ``Evolution of Defects and He within Grain Boundaries in Fe,'' MS\&T 2012, Microstructure-Based Property Prediction and Small Scale Experimental Validation: Microstructure Effects, OCT 9th, 2012, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, ``Career Mobility: Personal experience and lessons learned from industry, government laboratories, and academia,'' MS\&T 2012, Perspectives for Emerging Materials Professionals, 9 OCT 2012, Pittsburgh, PA.

\item 
\textbf{Barrett, C.D.}, {Tschopp, M.A.}, El Kadiri, H., ``Influence of Crystallographic Orientation on Twin Nucleation in Single Crystal Magnesium,'' International Conference on Plasticity 2012.

\item
\textbf{Solanki, K.N.}, {Tschopp, M.A.}, Rhodes, N.R., ``Atomic scale study of grain boundary segregation in Fe due to grain boundary morphology and point defects,''  Environmental Damage in Structural Materials Under Static/Cyclic Loads at Ambient Temperatures, Engineering Conferences International.

\item
\textbf{Tucker, G.J.}, {Tschopp, M.A.}, McDowell, D.L., ``Structure and Dislocation Nucleation in FCC GB Interfaces,'' Symposium on Structural Transitions and Local Deformation Processes At and Near Grain Boundaries, MS\&T 2009, Pittsburgh, PA.  

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``\href{http://dx.doi.org/10.13140/2.1.2238.0327}{KEYNOTE: Atomistic simulations of dislocation nucleation in FCC metals},'' Keynote lecture at 12th International Conference on Fracture 2009, `Atomistic Fracture and Deformation' symposium, 12--17 JUL 2009, Ottawa, Ontario, Canada.

\item
\textbf{Groeber, M.A.}, Fahringer, R., {Tschopp, M.A.}, Woodward, C., Dimiduk, D.M., Uchic, M., Rosenberger, A.H., ``Integration of 3D Structure Information for a Single X-tal Ni-Base Superalloy into Computational Models for Behavior Prediction,'' TMS 2009, San Francisco, CA.  

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Tension-compression asymmetry in homogeneous dislocation nucleation in single crystal copper,'' $14^{th}$ International Symposium on Plasticity 2009, `Atomistic and Multiscale Modeling of Dislocations and Defects in Solids' symposium, 3--8 JAN 2009, St.~Thomas, US Virgin Islands.

\item
\textbf{Spowart, J.E.}, Wilks, G.B., {Tschopp, M.A.}, ``Multi-Scalar Analysis of Area Fractions: Applications for Characterizing Multi-Component Discontinuously-Reinforced Composite Microstructures,'' 2008 MS\&T, OCT 5th-9th, 2008, Pittsburgh, PA.

\item
\textbf{Woodward, C.}, Groeber, M.A., {Tschopp, M.A.}, Uchic, M., Dimiduk, D.M., Russ, S., ``The Virtual Turbine Blade: Multi-Length Scale Characterization of a Single-Crystal Turbine Blade,'' MMM 2008, OCT 27th-31th, 2008, Tallahassee FL.

\item
{Tschopp, M.A.}, Tucker, G.J., Mayeur, J., \textbf{McDowell, D.L.}, ``Grain Boundary Structure, Properties and Implications for Dislocation/Disclination Mechanics in FCC Metals,'' IUTAM symposium, 5--9 NOV 2007, Eindhoven, Germany.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Dislocation Nucleation in Asymmetric Tilt Grain Boundaries,'' 13th International Symposium on Plasticity, JUN 2007, Alaska.

\item
\textbf{McDowell, D.L.}, \textbf{Tschopp, M.A.}, Tucker, G.J., ``Atomistic Modeling of Grain Boundary Structure and Dislocation Nucleation,'' Plenary lecture, MS\&T 2006, OCT 16th, 2006, Cincinnati, OH (invited plenary).

\item
\textbf{McDowell, D.L.}, Spearot, D.E., \textbf{Tschopp, M.A.},  ``Grain Boundary Structure and Dislocation / Disclination Mechanics in Plasticity of FCC Metals,''  2006 $12^{th}$ International Symposium on Plasticity, JUL 18th, 2006, Halifax, Nova Scotia.

\item
\textbf{McDowell, D.L.}, Spearot, D.E., Jacob, K.I., \textbf{Tschopp, M.A.},  ``Atomistic simulations of disclination structures and evolution in fcc metals,''  2006 Mathematisches Forschungsinstitut Oberwolfach `Mechanics of Materials', JAN 22nd--28th, 2006, Oberwolfach, Germany.

\end{cvlist}

\section{\sc Contributed Conference Presentations (Presenter, \\ Lead Author)}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Tschopp, M.A.}, ``ICME Challenges: New Approaches for Bridging Atomistic Length Scales through Interatomic Potential Evaluation and Design,'' ASME IMECE 2016, IMECE2016-68262, NOV 17, 2016.

\item
\textbf{Tschopp, M.A.}, Shawn Coleman, Srikanth Patala, Arash Banadaki, Zachary Trautt, ``Materials Databases: Grain Boundary Datasets for Quantifying Structure-Property Relationships,'' MS\&T 2016, OCT 24, 2016.

\item
\textbf{Tschopp, M.A.}, ``Influence of Grain Boundary Structure on Segregation of Point Defects, Helium, and Hydrogen,'' ASME IMECE 2016, IMECE2016-68261.  

\item
\textbf{Tschopp, M.A.}, ``ICME Challenges: New Approaches for Bridging Atomistic Length Scales through Interatomic Potential Evaluation and Design,'' ASME IMECE 2016, IMECE2016-68262.

\item
\textbf{Tschopp, M.A.}, Efrain Hernandez, Shawn Coleman, Souma Chowdhury, ``A Metamodeling Approach for Parameter Sensitivity Analysis and Uncertainty Quantification in a Boron-Carbide Interatomic Potential,'' MS\&T 2016.

\item
\textbf{Tschopp, M.A.}, Shawn Coleman, Srikanth Patala, Arash Banadaki, Zachary Trautt, ``Materials Databases: Grain Boundary Datasets for Quantifying Structure-Property Relationships,'' MS\&T 2016.

\item
\textbf{Tschopp, M.A.}, Coleman, S.P., Synowczynski-Dunn, J., Solanki, K.N., McDowell, D.L., ``Atomistic Modeling of Structure-Property Relationships in Grain Boundaries,'' TMS 2016, FEB 14--18, 2016, Nashville, TN.

\item
\textbf{Tschopp, M.A.}, Coleman, S.P., ``Towards a Data Repository for Atomistic Modeling and Simulation of Grain Boundaries,'' NIST Workshop, 23 NOV 2015.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Gao, F., Coleman, S., Dunn, J.,  ``Atomistic Modeling for Grain Boundary (Segregation) Engineering: Exploiting Micro- and Macro-Scale Interfacial Structure-Property Relationships,'' TMS 2015, Polycrystalline Materials: Bringing Together Experiments, Simulations, and Analytic Theories symposium, MAR 17, 2015, Lake Buena Vista, FL.

\item
\textbf{Tschopp, M.A.}, Oppedal, A., Solanki, K.N., ``Local/Global Measurement of Primary Dendrite Arm Spacing in Single Crystal Nickel-Based Superalloys,'' TMS 2015, Multiscale Microstructure, Mechanics, and Prognosis of High Temperature Alloys symposium, MAR 16, 2015, Lake Buena Vista, FL.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Gao, F.,  ``Energetics and length scales of point defect and element segregation to grain boundaries,'' MS\&T 2014, Interfaces, Grain Boundaries, and Surfaces from Atomistic and Macroscopic Approaches symposium, OCT 14, 2014, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, Kecskes, L., Atwater, M.A., Hammond, V., Darling, K.A., ``Equal Channel Angular Extrusion Consolidation of Lightweight High Entropy Alloys,''  TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Yin, W., Darling, K.A., Kecskes, L., Wei, Q., ``Quasi-static and Dynamic Mechanical Properties of Nanostructured Copper Doped with Tantalum,''  TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Oppedal, A., Miller, J.D., Carino, R., Groeber, M.A., Rosenberger, A.H., Solanki, K.N., ``Characterizing Primary Dendritic Microstructures to Quantify the Processing-Structure-Property Relationship in Single Crystal Nickel-Based Superalloys,'' TMS 2013, Characterization of Minerals, Metals and Materials 2013, MAR 6th, 2013, San Antonio, TX.

\item
\textbf{Tschopp, M.A.}, Gao, F., Solanki, K.N., Sun, X., ``Influence of Grain Boundary Structure on Segregation of Cr/He atoms in Fe,'' TMS 2013, Integrated Computational Modeling of Materials for Nuclear Energy symposium, MAR 5th, 2013, San Antonio, TX.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Rhodes, N.R., ``Energetics of point defect and impurity segregation to grain boundaries in $\alpha$-Fe,'' TMS 2012 Annual Meeting \& Exhibition, MAR 11th--15th, 2012, Orlando, FL.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Horstemeyer, M.F., Baskes, M.I., Gao, F., Sun, X., Khaleel, M., ``Effect of grain boundary character on the segregation of impurities and point defects to grain boundaries in Fe,'' Deformation and Transitions at Grain Boundaries, MS\&T 2011, OCT 16th--20th, 2011, Columbus, OH.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Horstemeyer, M.F., ``A generalized framework for quantifying grain boundary structure-property relationships at the nanoscale,'' Interfaces, Grain Boundaries and Surfaces from Atomistic and Macroscopic Approaches -- Fundamental and Engineering Issues, MS\&T 2011, OCT 16th--20th, 2011, Columbus, OH.

\item
\textbf{Tschopp, M.A.} ``Image Analysis of Microstructure Features,'' Severstal Visit, MAY 2011, Starkville, MS.

\item
\textbf{Tschopp, M.A.}, Solanki, K.N., Horstemeyer, M.F., Baskes, M.I., Gao, F., Sun, X., Khaleel, M., ``Towards a unified framework for interatomic potential development: Application to the Fe-He system,''  TMS 2011, Microstructural Processes in Irradiated Materials symposium, FEB 27th--MAR 3rd, 2011, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Ward, D.K., Bouvard, J.L., Horstemeyer, M.F., ``Atomic Scale Deformation Mechanisms of Amorphous Polyethylene under Tensile Loading,'' TMS 2011, Massively Parallel Simulations of Materials Response symposium, FEB 27th--MAR 3rd, 2011, San Diego, CA.

\item
\textbf{Tschopp, M.A.}, Horstemeyer, M.F., Gao, F., Sun, X., Khaleel, M., ``Influence of Grain Boundary Character on Point Defect Formation Energies in BCC Fe,'' MS\&T 2010, Phase Stability, Diffusion, Kinetics and Their Applications (PSDK-V) Symposium,  OCT 21st, 2010, Houston, TX.

\item
\textbf{Tschopp, M.A.}, Groeber, M., Simmons, J.P., Rosenberger, A.H., Woodward, C., ``Development of Imaging Techniques for Automated Extraction of Microstructural Features from Serial Images,'' MS\&T 2010, Tools, Models, Databases and Simulation Tools Developed and Needed to Realize the Vision of Integrated Computational Materials Engineering Symposium, OCT 20th, 2010, Houston, TX.

\item
\textbf{Tschopp, M.A.}, Horstemeyer, M.F., ``Computational framework for grain boundary struc\-ture-property relationships at the nanoscale,'' MS\&T 2010, Tools, Models, Databases and Simulation Tools Developed and Needed to Realize the Vision of Integrated Computational Materials Engineering Symposium, OCT 19th, 2010, Houston, TX.

\item
\textbf{Tschopp, M.A.}, Groeber, M., Simmons, J.P., Rosenberger, A.H., Woodward, C., ``Automated Dendrite Core Detection in Single Crystal Ni-Based Superalloys from Optical Images,'' MS\&T 2009, Microstructure Characterization, Analyses, and Design Symposium, OCT 25th--29th, 2009, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, Wilks, G.B., Spowart, J.E., ``Multi-Scale Analysis of Area Fractions Characterization of Two-Phase Composite Microstructures,'' ASME IMECE 2009, Novel Approaches in Heterogeneous Materials Analysis and Characterization Symposium, NOV 13th--19th, 2009, Lake Buena Vista, FL.

\item
\textbf{Tschopp, M.A.}, Spearot, D.E., McDowell, D.L., ``Molecular Dynamics Simulation of Homogeneous Nucleation of Dislocations in Single Crystals,'' ASME IMECE 2009, Symposium on Modeling at Atomic / Molecular Scale, NOV 13th--19th, 2009, Lake Buena Vista, FL.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Asymmetric tilt grain boundary structure in copper and aluminum,'' 2008 MS\&T, OCT 5th--9th, 2008, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, Wilks, G., Spowart, J.E., ``Multi-Scale Characterization of Orthotropic Microstructures,'' 2008 MS\&T, OCT 5th--9th, 2008, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Atomistic Simulations of Grain Boundary Dislocation Nucleation,'' 2008 TMS Annual Meeting \& Exhibition, MAR 9th--13th, 2008, New Orleans, LA.

\item
\textbf{Tschopp, M.A.}, Tiwari, S., Ghosh, S., McDowell, D.L., ``Influence of Grain Boundary Character on Nanocrystalline Plasticity,'' 2008 TMS Annual Meeting \& Exhibition, MAR 9th--13th, 2008, New Orleans, LA.

\item
\textbf{Tschopp, M.A.}, Medlin, D.E., McDowell, D.L., ``Dislocation Nucleation at the Vicinal Coherent Twin in FCC Cu and Al,'' 2008 TMS Annual Meeting \& Exhibition, MAR 9th--13th, 2008, New Orleans, LA.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Structures, Energies, and Dislocation Nucleation of $\Sigma3$ Asymmetric Tilt Grain Boundaries,'' TMS Conference 2007, FEB 26th, 2007, Orlando, FL.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Microrotation-Augmented Energy-Minimization for Generating 3D Nanocrystalline Cu Structures'' and ``Structures and Energies of $\Sigma3$ Asymmetric Tilt Grain Boundaries,''  16th European Conference of Fracture, JUL 4th, 2006, Alexandroupolis, Greece.

\item
\textbf{Tschopp, M.A.}, McDowell, D.L., ``Microrotation-Augmented Energy-Minimization for Generating Nanocrystalline Cu Structures,''  2005 ASME IMECE, NOV 8th, 2005, Orlando, FL.

\item
\textbf{Tschopp, M.A.}, Wang, Q.G., DeWyse, M.J., ``Mechanisms of Misrun Formation in Aluminum Lost Foam Castings,''  AFS 106th Casting Congress - Lost Foam Casting Division 11, MAY 2002, Minneapolis, MN.

\item
\textbf{Tschopp, M.A.}, ``Fluidity of Aluminum A356 in the Lost Foam Casting Process,''  AFS 106th Casting Congress - Lost Foam Casting Division 11, MAY 2002, Minneapolis, MN.

\item
\textbf{Tschopp, M.A.}, ``Water Jacket Leakers - Intake Spring Deck Fold and Intake Port \#12 Fold Defects,''  GM Lost Foam Technology Exchange, OCT 2001, Saginaw, MI.

\item
\textbf{Tschopp, M.A.}, Ramsay, C.W., Askeland, D.R., ``Mechanisms of Formation of Pyrolysis Defects in Aluminum Lost Foam Castings''  AFS 104th Casting Congress - Lost Foam Casting Division 11, APR 2000, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, Ramsay, C.W., Askeland, D.R., ``Processing Variable Significance on Metal Flow and Defect Formation in Thick Section LFCs - Full Factorial Experiment,''  AFS 104th Casting Congress - Lost Foam Casting Division 11, APR 2000, Pittsburgh, PA.

\item
\textbf{Tschopp, M.A.}, Askeland, D.R., ``Mechanisms of Formation of Pyrolysis Defects in Aluminum Lost Foam Castings,''  DOE Lost Foam Consortium \& Division 11 AFS Meeting, OCT 1999, Des Plaines, IL.

\end{cvlist}

\section{\sc Conference Presentations (Co-Author)}

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Patala, S.}, {Tschopp, M.A.}, ``An efficient Monte-Carlo algorithm for determining the minimum energy structures of metallic grain boundaries,'' TMS 2018, MAR 12, 2018.

\item
\textbf{Paul, J.}, Limmer, K., {Tschopp, M.A.}, Chaudhuri, S., ``Searching for Corrosion Resistant Mg Alloys Using Genetic Algorithms,'' TMS 2018, MAR 12, 2018.

\item
\textbf{Dickel, D.}, {Tschopp, M.A.}, Horstemeyer, M.F., ``Calibration of a Titanium Modified Embedded Atom Method Potential to High Temperature Behavior,''  TMS 2018, MAR 13, 2018.

\item
\textbf{Paudel, Y.R.}, Barrett, C.D., {Tschopp, M.A.}, Inal, K., El Kadiri, H., ``A Micromechanical Study for Twin Nucleation in hcp Metals: Development of Analytical Solution to Study Twin Bands Formation,''  TMS 2018, MAR 15, 2018.

\item
\textbf{Patala, S.}, {Tschopp, M.A.}, ``An efficient Monte-Carlo algorithm for determining the minimum energy structures of interfaces,'' MRS 2017 Fall Conference, 11/27/17.

\item
\textbf{Paudel, Y.R.}, {Tschopp, M.A.}, El Kadiri, H., et al., ``An Analytical Micromechanical Model Solution for Twin Nucleation in Hexagonal Close-packed Metals,'' MS\&T 2017, 10/11/2017.

\item
\textbf{Hornbuckle, B.C.}, {Tschopp, M.A.}, Roberts, A.J., Darling, K.A., et al., ``Utilizing Site Specific Shear Punch Testing to Evaluate Friction Stir Welded Al-2139 T8 Plate,'' MS\&T 2017, 10/12/2017.

\item
\textbf{Limmer, K.}, {Tschopp, M.A.}, McWilliams, B., et al.~``Design of Experiments Approach for DMLS,'' MS\&T 2017, 10/9/2017.

\item
\textbf{Goins, P.}, {Tschopp, M.A.}, ``Magnetic Fields and Thermal Gradients: Simulated Engineering of Three-Dimensional Microstructure through Thermomagnetic Manipulation,'' MS\&T 2017, 10/12/2017.

\item
\textbf{Hern\'andez--Rivera, E.}, {Tschopp, M.A.}, ``Modeling Viscoplastic Deformation of Synthetic Welded Microstructures,'' MS\&T 2017, 10/12/2017.

\item
\textbf{Khanzadeh, M.}, Tschopp, M.A., Bian, L., ``Classification based porosity prediction technique using melt pool signal,'' 2017 Annual International Solid Freeform Fabrication Symposium (SFF Symp 2017), 08/09/2017.  

\item
\textbf{Hern\'andez--Rivera, E.}, Chowdhury, S., Tschopp, M.A., Coleman, S., ``Design of Experiments Approach to Optimizing Complex Bond Order and Reactive Potentials,'' TMS 2017, FEB 27, 2017.

\item
\textbf{Aboutaleb, A.}, Bian, L., Rao, P.K., Tschopp, M.A., ``Accelerated Geometry Accuracy Optimization of Additive Manufacturing Parts,'' ASME Manufacturing Science and Engineering Conference (MSEC2017), JUN 2017.

\item
\textbf{M. Khanzadehdaghalian}, Chowdhury, S., Tschopp, M.A., Bian, L.,``Anomaly Detection of Additively Manufactured Thin-Wall Using 3-D Modeling of Melt Pool Temperature Distribution,'' ASME Manufacturing Science and Engineering Conference (MSEC2017), JUN 2017.

\item
\textbf{Hern\'andez--Rivera, E.}, Tschopp, M.A., Coleman, S., Taylor, D., Subhash, G., Parsard, G., ``Similarity Metrics Analysis of B$_4$C Polymorphic Structural Differences As Measured From Virtual XRD,'' MACH Conference 2017.

\item
\textbf{Hern\'andez--Rivera, E.}, Tschopp, M.A., Baskes, M.I., ``MEAM Parameter Space Optimization for Elemental Boron,'' International Conference \& Exposition on Advanced Ceramics \& Composites, JAN 2017, Daytona Beach, FL.

\item
\textbf{Hern\'andez--Rivera, E.}, Coleman, S., Tschopp, M.A., ``Quantifying Similarities Between Gaussian–based Spectral Responses and its Application to Virtual Materials Characterization,'' International Conference \& Exposition on Advanced Ceramics \& Composites, JAN 2017, Daytona Beach, FL.

\item
\textbf{Dongare, A.M.}, Chen, J., Tschopp, M.A.,  ``Spall Failure Response of Nanocrystalline Cu-Ta Systems at the Atomic Scales,'' ASME IMECE 2016, NOV 14, 2016.

\item
\textbf{Banadaki, A.}, Tschopp, M.A., Patala, S., ``An Efficient Algorithm for Determining the Minimum Energy Structures of Grain Boundaries,'' MS\&T 2016, OCT 24, 2016.

\item
\textbf{Chen, J.}, Tschopp, M.A., Dongare, A.M., ``Effect of Solute on the Shock and Spall Failure Response of Nanocrystalline Cu-Ta Systems at the Atomic Scales,'' ASME IMECE 2016.

\item
\textbf{Foley, D.}, Coleman, S., Tschopp, M.A., Tucker, G.J., ``Linking Nanoscale Deformation Mechanisms and Interfaces with Diffraction Profiles in Nanocrystalline Materials,'' MS\&T 2016.

\item
\textbf{Hern\'andez--Rivera, E.}, Tschopp, M.A., Allen, J.B., ``Implementation of a coupled Read--Shockley Q--state Monte Carlo into the SPPARKS framework to Simulate Magnetic Field Influence on Textures,'' MS\&T 2016.

\item
\textbf{Hern\'andez--Rivera, E.}, Coleman, S.P., Tschopp, M.A., ``Sensitivity Analysis of the ReaxFF Parameter Space,' ' SIAM Conference on Mathematical Aspects of Materials Science (MS16), MAY 8--12, 2016, Philadelphia, PA.

\item
\textbf{Rajagopalan, M.}, Turnage, S., Darling, K.,  Tschopp, M.A., Solanki, K.N., ``Microstructural Evolution of Nanocrystalline Copper-tantalum Alloy,'' TMS 2016, FEB 14--18, 2016, Nashville, TN.

\item
\textbf{Turnage, S.}, Darling, K., Rajagopalan, M., Tschopp, M.A., Solanki, K.N., ``Dynamic Behavior of a Nanocrystalline Cu-Ta Alloy,'' TMS 2016, FEB 14--18, 2016, Nashville, TN.

\item
\textbf{Coleman, S.P.}, Tschopp, M.A., Synowczynski-Dunn, J., ``Building, Optimizing and Characterizing Grain Boundaries in Atomistic Simulations,'' TMS 2016, FEB 14--18, 2016, Nashville, TN.

\item
\textbf{Bhatia, M.}, Solanki, K.N., Tschopp, M.A., ``MEAM potential for Boron Suboxide (B$_6$O),'' TMS 2016, FEB 14--18, 2016, Nashville, TN.

\item
\textbf{Turnage, S.}, Rajagopalan, M., Darling, K., Solanki, K., Tschopp, M.A., ``Dynamic Behavior and Microstructural Evolution of Nanocrystalline and Ultrafine Grained Cu-Ta Alloys,''  TMS 2016, FEB 14--18, 2016, Nashville, TN.

\item
\textbf{Synowczynski-Dunn, J.}, Tschopp, M.A., Coleman, S.P., ``First Principles Study of Defect Formation in Bulk Boron Suboxide,'' International Conference \& Exposition on Advanced Ceramics \& Composites, JAN 26, 2016, Daytona Beach, FL (poster presentation).

\item
\textbf{Foley, D.}, Coleman, S.P., Tschopp, M.A., ``Study of Nanocrystalline Deformation Using Virtual Diffraction Characterization,'' 23rd ARL/USMA Technical Symposium, OCT 14, 2015 (poster presentation).

\item
\textbf{Hern\'andez--Rivera, E.}, Coleman, S.P., Tschopp, M.A., ``Hybrid Deterministic-Statistical Models for Mesoscale Microstructural Evolution,'' 23rd ARL/USMA Technical Symposium, OCT 14, 2015 (poster presentation).

\item
\textbf{Coleman, S.P.}, Synowczynski-Dunn, J., Hernandez, E., Tschopp, M.A., ``Modeling Boron Ceramics: Defects and Interfaces,'' MEDE Fall Meeting, OCT 15, 2015, White Marsh, MD (poster presentation).

\item
\textbf{Hern\'andez--Rivera, E.}, Coleman, S.P., Tschopp, M.A., ``Hybrid Deterministic-Statistical Models for Mesoscale Microstructural Evolution,'' MEDE Fall Meeting, OCT 15, 2015, White Marsh, MD (poster presentation).

\item
\textbf{Shi, J.Y.}, Gao, F., Peng, L., Ye, M.Y., Tschopp, M.A., ``Computational Study of Grain Boundary Interactions with Helium Under Tensile Stress in Alpha-Iron,'' ICFRM17, OCT 12--16, 2015, Aachen, Germany.

\item
\textbf{Coleman, S.P.}, Synowczynski-Dunn, J., Tschopp, M.A., ``Grain Boundary Builder for Atomistic Simulations,'' MS\&T 2015, OCT 8, 2015, Columbus, OH.

\item
\textbf{Synowczynski-Dunn, J.}, Tschopp, M.A., Coleman, S.P.,  ``Density Functional Theory Study of Vacancy Formation in B$_6$O,'' MS\&T 2015, OCT 6, 2015, Columbus, OH (poster presentation).

\item
\textbf{Coleman, S.P.}, Tucker, G.J., Tschopp, M.A., ``Decomposing Nanocrystalline Deformation Using Virtual Diffraction,'' MS\&T 2015, OCT 7, 2015, Columbus, OH.

\item
{\textbf{Coleman, S.}}, Tschopp, M.A.,  ``Virtual Diffraction: A Technique for Coupling Atomistic Simulations and Experiments,'' MACH Conference 2015, In-situ, Time-resolved Measurements and Computational Modeling symposium, APR 8th, 2015, Annapolis, MD.

\item
{\textbf{Rajagopalan, M.}}, Adlakha, I., Muthegowda, N., Solanki, K.N., Tschopp, M.A., ``Energetics Associated with the Interaction between Embrittlement Species and Grain Boundaries in Alpha-Iron,'' TMS 2015, Materials and Fuels for the Current and Advanced Nuclear Reactors IV symposium, MAR 19, 2015, Lake Buena Vista, FL.

\item
\textbf{Solanki, K.N.}, Bhatia, M., Zhang, X., Azarnoush, M., Lu, G., Tschopp, M.A., ``Role of Oxygen on Mechanical Properties of High Temperature Materials: A QM/MM Study,'' TMS 2015, Multiscale Microstructure, Mechanics, and Prognosis of High Temperature Alloys symposium, MAR 18, 2015, Lake Buena Vista, FL.

\item
\textbf{Turnage, S.}, Darling, K.A., Rajagopalan, M., Tschopp, M.A., Solanki, K.N., ``Dynamic Behavior of a Nanocrystalline Cu--Ta Alloy,'' TMS 2015, Polycrystalline Materials: Bringing Together Experiments, Simulations, and Analytic Theories symposium, MAR 16, 2015, Lake Buena Vista, FL.

\item
\textbf{Hornbuckle, C.}, Kecskes, L.J., Darling, K.A., Tschopp, M.A., Tanaporn, R., Banerjee, R., Pun, G.P., Mishin, Y., ``Microstructure and Mechanical Properties of Bulk Nanostructured Cu--Ta Alloys Consolidated by Equal Channel Angular Extrusion,'' TMS 2015, Novel Synthesis and Consolidation of Powder Materials symposium, MAR 16, 2015, Lake Buena Vista, FL.

\item
\textbf{Nouranian, S.}, Gwaltney, S.R., Baskes, M.I., Tschopp, M.A., Horstemeyer, M.F., ``Computational Nanomechanics of Single-Chain Molecular Bond Rupture in Hydrocarbon-Based Polymers Using Modified Embedded Atom Method Potential,''  TMS 2015, Computational Modeling and Stochastic Methods in Materials Discovery and Properties symposium, MAR 16, 2015, Lake Buena Vista, FL.

\item
\textbf{Nouranian, S.}, Baskes, M.I., Gwaltney, S.R., Tschopp, M.A., Horstemeyer, M.F., ``An Interatomic Potential for the Interfacial Characterization of Titanium and Polyethylene Based on the Modified Embedded-Atom Method,'' 14th AIChE Annual Meeting 2014, NOV 17, 2014, Atlanta, GA.

\item
\textbf{Turnage, S.}, Solanki, K.N., Whittington, W., Florea, R., Tschopp, M.A., Darling, K.A., ``Structure-property relationships of 6061-T6 aluminum alloy thermo-mechanically bonded with varying temperatures,'' ASME 2014, Montreal, Quebec, Canada.

\item
\textbf{Atwater, M.A.}, Darling, K.A., Tschopp, M.A., ``Solid-state Foaming with Additive Expansion: A Simple Method for Teaching Old Dogs New Tricks,'' MS\&T 2014, Advanced Manufacturing Technologies -- Advanced Manufacturing III symposium, OCT 15, 2014, Pittsburgh, PA.

\item
\textbf{Atwater, M.A.}, Darling, K.A., Tschopp, M.A., Murdoch, H.A., Kecskes, L.J., ``Stabilization and Mechanical Properties of Nanocrystalline Copper by Alloying with Tantalum,'' MS\&T 2014, Sintering and Related Powder Processing Science and Technologies symposium, OCT 15, 2014, Pittsburgh, PA.

\item
\textbf{Rajagopolan, M.}, Bhatia, M.A., Solanki, K.N., Tschopp, M.A., ``Investigation of Atomic-Scale Energetics on Liquid Metal Embrittlement of Aluminum due to Gallium,'' TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Murdoch, H.A.}, Darling, K.A., Tschopp, M.A., Roberts, A.J., Cook, T., ``Grain refinement and growth in copper using surface mechanical attrition treatment at cryogenic temperatures,''  TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Turnage, S.}, Solanki, K.N., Whittington, W., Florea, R., Tschopp, M.A., Darling, K.A., ``Structure-property relationship investigation of a thermo-mechanical-electrical processed spot weld,'' TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Asadi, E.}, Zaeem, M.A., Moitra, A., Tschopp, M.A., ``Effects of vacancies on the generalized stacking fault energy of metals,'' TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Adlakha, I.}, Solanki, K.N., Tschopp, M.A., ``Atomic scale investigation of grain boundary structure role on deformation and crack growth dynamics in aluminum,'' TMS 2014, FEB 16--20, 2014, San Diego, CA.

\item
\textbf{Nouranian, S.}, Tschopp, M.A., Gwaltney, S.R., Baskes, M.I.,  Horstemeyer, M.F., ``Simulations of bond rupture in normal alkanes under tensile molecular deformation using reactive potentials,'' AIChE 2013, NOV 3--8, 2013, San Francisco, CA.

\item
\textbf{Nouranian, S.}, Tschopp, M.A., Gwaltney, S.R., Baskes, M.I.,  Horstemeyer, M.F., ``A Reactive Interatomic Potential for the Molecular Dynamics Simulations of Saturated Hydrocarbons Using the Modified Embedded-Atom Method,'' AIChE 2013, NOV 3--8, 2013, San Francisco, CA.

\item
Bhattia, M., Adlakha, I., \textbf{Solanki, K.N.}, Tschopp, M.A., ``Influence of Hydrogen and Point Defects in BCC Iron: A nanoscale investigation,'' TMS 2013, Microstructural Processes in Irradiated Materials symposium, MAR 4th, 2013, San Antonio, TX. 

\item
\textbf{Spear, P.}, Akasheh, F., Tschopp, M.A., Li, B., ``Atomistic Generalized Stacking Fault Energy Curve for Metallic Elements at the Interface,'' Regional Undergraduate Research Symposium at Albany State University, OCT 24th-25th, 2012, Albany, GA.

\item
\textbf{Wright, T.}, Akasheh, F., Tschopp, M.A., Li, B., ``Identification of the Dislocation structure in Nanoscale Metallic Interfaces,'' Regional Undergraduate Research Symposium at Albany State University, OCT 24th-25th, 2012, Albany, GA.

\item
\textbf{Zhang, X.E.}, Tschopp, M.A., Shi, S., Cao, J., ``The Strain-stress Behavior of Amorphous Cellulose from Molecular Dynamics Simulation,'' 2012 International Conference on Green Power, Materials and Manufacturing Technology and Applications (GPMMTA 2012), JUL 17th-19th, 2012, Kunming, Yunnan, China.

\item
\textbf{Solanki, K.N.}, Tschopp, M.A., Rhodes, N.R., ``Nanoscale investigation of segregation and embrittlement in $\alpha$-Fe due to hydrogen and grain boundary character,'' TMS 2012 Annual Meeting \& Exhibition, MAR 11th--15th, 2012, Orlando, FL.

\item
\textbf{Adlakha, I.}, Solanki, K.N., Moitra, A., Tschopp, M.A., ``Influence of Size on Strength of Nickel Nanowires,'' TMS 2012 Annual Meeting \& Exhibition, MAR 11th--15th, 2012, Orlando, FL.

\item
\textbf{Bhattia, M.}, Solanki, K.N., Moitra, A., Tschopp, M.A., ``Role of substitution elements on twinning nucleation mechanism in Magnesium,'' Deformation, Damage, and Fracture of Light Metals and Alloys, TMS 2012 Annual Meeting \& Exhibition, MAR 11th--15th, 2012, Orlando, FL.

\item
\textbf{Adlakha, I.}, Solanki, K.N., Moitra, A., Tschopp, M.A., ``A nanoscale investigation on the effect of Hydrogen in confined volumes,'' TMS 2012 Annual Meeting \& Exhibition, MAR 11th--15th, 2012, Orlando, FL.

\item
\textbf{Asafa, O.}, Stone, T., Tschopp, M.A., Gullett, P., Horstemeyer, M.F., ``Molecular Dynamics Study of Frictional Effects on the Compaction of Metal Nanoparticles,'' Multi Scale Modeling of Microstructure Deformation in Material Processing, MS\&T 2011, OCT 16th--20th, 2011, Columbus, OH.

\item
Moitra, A., \textbf{Solanki, K.N.}, Bhattia, M., Tschopp, M.A., ``Orientation effect on dislocation nucleation and related interaction during void growth simulations in Aluminum,'' 11th US National Congress on Computational Mechanics, JUL 25th--28th, 2011, Minneapolis, MN.

\item
\textbf{Bouvard, J.L.}, Tschopp, M.A., Bammann, D., Horstemeyer, M.F., ``Multiscale Modeling of Amorphous Polymers: from Molecular Dynamic Simulations to Continuum Models,'' 11th US National Congress on Computational Mechanics, Computational science of soft matter in extreme environments: from molecules to finite elements symposium, JUL 25th--28th, 2011, Minneapolis, MN.

\item 
\textbf{Bouvard, J.-L.}, {Tschopp, M.A.}, Bouvard, C., Denton, B., Horstemeyer, M.F., ``Simulation of Impact Tests on Polycarbonate at Different Strain Rates and Temperatures,'' SEM 2011, JUN 13th--16th, 2011, Uncasville, CT.

\item
\textbf{Zhang, X.E.}, Tschopp, M.A., Shi, S., Cao, J., ``Molecular Dynamics Simulations of Deformation in Amorphous Cellulose,'' 11th International Conference on Wood \& Biofiber Plastic Composites, Nanotechnology in Wood Composites Symposium, MAY 16th--17th, 2011, Madison, WI.

\item
\textbf{Liyanage, L.}, Houze, J., Kim, S.-G., Tschopp, M.A., Kim, S., Baskes, M.I., Horstemeyer, M.F., ``Modified Embedded Atom Method potential for Fe-C system,'' APS MAR Meeting 2011, Session L35: Metals: Alloys and Impurities, MAR 21st--25th, 2011, Dallas, TX.

\item 
\textbf{Barrett, C.D.}, Tschopp, M.A., El Kadiri, H., Li, B., ``Influence of Crystallographic Orientation on Twin Nucleation in Single Crystal Magnesium,'' TMS 2011, Magnesium Technology 2011 symposium, FEB 27th--MAR 3rd, 2011, San Diego, CA.

\item
\textbf{Bhattia, M.A.}, Solanki, K.N., Moitra, A., Tschopp, M.A., ``The effect of crystallographic orientation on void growth: A molecular dynamics study,'' TMS 2011, Deformation, Damage, and Fracture of Light Metals and Alloys symposium, FEB 27th--MAR 3rd, 2011, San Diego, CA.

\item
Lugo, M., Tschopp, M.A., Jordan, J.B., \textbf{Horstemeyer, M.F.}, ``Microstructure relationship in the damage evolution process of an AZ61 magnesium alloy,'' TMS 2011, Magnesium Technology 2011 symposium, FEB 27th--MAR 3rd, 2011, San Diego, CA.

\item
\textbf{Bhattia, M.}, Tschopp, M.A., Solanki, K., Horstemeyer, M.F., ``Influence of Crystallographic Orientation on void growth in Al,'' MS\&T 2010, Multi-Scale Modeling of Microstructure Deformation in Material Processing Symposium, OCT 17th--21st, 2010, Houston, TX.

\item
Tschopp, M.A., \textbf{Tucker, G.J.}, McDowell, D.L., ``Atomistic Simulations of Dislocation Nucleation in Copper Grain Boundaries under Uniaxial Tension and Compression,'' 2008 TMS Annual Meeting \& Exhibition,  MAR 9th--13th, 2008, New Orleans, LA.

\item
\textbf{Wilks, G.B.}, Tschopp, M.A., Spowart, J.E., ``Directional Multi-Scale Analysis of Area Fractions,'' 2008 MS\&T, OCT 5th--9th, 2008, Pittsburgh, PA.

\item
\textbf{Tucker, G.J.}, Tschopp, M.A., McDowell, D.L., ``Atomistic Simulations of Free Volume in $\left\langle100\right\rangle$ and $\left\langle110\right\rangle$ Tilt Grain Boundaries in Cu and Al,'' TMS Conference, FEB 27th, 2007, Orlando, FL.

\item
\textbf{McDowell, D.L.}, Tschopp, M.A., Spearot, D.E.,  ``Atomistic Simulations of Grain Boundary Structure and Evolution in FCC Metals,''  MRS Conference, NOV 28th, 2005, Boston, MA.

\end{cvlist}

