\section{\sc Short Course Presentations}

Over the past several years, over 3000 people from around the world (majority DoD) have registered for several machine learning, artificial intelligence, and data science short courses (from 1--2 days to 1--2 weeks) that I developed and taught virtually and in-person, teaching the basic concepts, math, and algorithms in these areas starting from linear algebra through convolutional neural networks, autoencoders and generative adversarial networks, sequence models, natural language processing, and transformers---presented in both Python scripting as well as in Excel. 

\begin{cvlist}
\setlength{\itemsep}{0in}
\setlength{\parsep}{0in} 
\setlength{\parskip}{0in}
\setlength{\topsep}{0in} 
\setlength{\partopsep}{0in} 
\setlength{\leftmargin}{0.2in}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Fourth Be With You!,'' Microsoft TEAMS, 4--5 MAY 2026 (16-h total).
\begin{list2}
\item[$\star$] Sixth and final iteration of the course; $\approx$370 registered participants.
\item[$\star$] Post-course survey (n=21): overall course 4.63/5.0, instructor 4.95/5.0.
\item[$\star$] ``Truly, one of the best courses I've taken... Very entertaining, engaging, educational and excellent, the four E's.''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Course Be With You,'' Microsoft TEAMS, 1--2 MAY 2025 (16-h total).
\begin{list2}
\item[$\star$] $>$350 registered participants.
\item[$\star$] ``AWESOME!'', ``Excellent course! I've walked away with a better understanding of what ML is and how to set it up'', ``Fantastic course. Thank you for all the foundational knowledge to catch up with how the field has changed over the last 10 years.''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Army HQ Strategic Broadening Seminar: AI for Soldiers,'' 1 Week In-Resident Course, 7-11 APR 2025 (40-h total).
\begin{list2}
\item[$\star$] Led development and planning for course, adapting course to 1 week.  Taught one day ML crash course.
\item[$\star$] $>$29 Soldiers and civilians from bases around the country.
\item[$\star$] Comments: ``The instructors were fantastic.  They brought interest into every concept and found a way to bring us back to the ```so what'' of how learning the algorithms and math and concepts woudl better assist us in using AI/ML.'', ``Thank you! The course was excellent.''
\item[$\star$] ``\href{https://www.army.mil/article/285626/army_scientists_train_soldiers_on_how_to_leverage_ai_technologies}{Army scientists train Soldiers on how to leverage AI technologies},'' ARL Public Affairs, 19 MAY 2025.
\item[$\star$] ``Artificial Intelligence for Soldiers 2025: Enhancing AI Readiness for the Army,'' ARL-SR-0506 (JUN 2025) 1-79.
\item[$\star$] Requested by Army HQDA for 2 courses in FY26
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Artificial Intelligence 101: A Gentle Introduction to AI,'' Rock Island Arsenal, AMC Army Sustainment Command HQ, 10-11 DEC 2024 (10-h total).
\begin{list2}
\item[$\star$] Capstone course for AMC-ASC's month-long Data Literacy training series.
\item[$\star$] $>$40 registered in-person participants.
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning 101,'' Rock Island Arsenal, AMC Joint Munitions Command HQ, 24-26 SEP 2024 (20-h total).
\begin{list2}
\item[$\star$] $>$30 registered in-person participants.
\item[$\star$] Comments: ``Fantastic course'', ``Great Class, 10/10 recommended'', ``Probably one of the best multi-day presentations in terms of keeping engaged...''
\item[$\star$] BG Ronnie Anderson Jr., JMC's Commander, recognized Dr.~Tschopp with an award
\item[$\star$] ``\href{https://www.dvidshub.net/news/484157/operationalizing-science-jmc-with-artificial-intelligence-and-machine-learning}{Operationalizing Science at JMC with Artificial Intelligence and Machine Learning},'' Joint Munitions Command Public Affairs.
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Fourth Be With You,'' Microsoft TEAMS, 2--3 MAY 2024 (16-h total).
\begin{list2}
\item[$\star$] $>$300 registered participants, 4800 person-hours of ML instruction.
\item[$\star$] ``I'm taking some training on Machine Learning from ARL.  This guy is delightfully obsessed with Star Wars.  The course opened with script rolling up the screen.  It has theme music for opening and breaks. He is wearing a Jedi cloak and occassionally brandishes a light saber.  Don't end your government career without experiencing something like this.  P.S. Oh, and the course content and delivery is phenomenal.  It's making me feel smarter.''
\item[$\star$] ``The course was fabulous and it demystified ML for me! The instructor is extremely knowledgeable regarding ML. This is one of the best courses I have taken. A ton of material was presented and the instructor made it understandable and interesting. The Star Wars examples made the class fun as well :-) The instructor provided many references and tips on where to find additional information regarding our future ML endeavors. Many thanks to the instructor for all the time and effort put in and to offer the course.''
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Army HQ Strategic Broadening Seminar: AI for Soldiers,'' 2 Week In-Resident Course, 8-19 APR 2024 (80-h total).
\begin{list2}
\item[$\star$] Only Strategic Broadening Seminar course selected by Army HQ that is taught within the federal government.
\item[$\star$] Led development and planning for pilot course, which involved coordination of $\approx$100 people.  Taught multiple days of instruction on AI and ML.
\item[$\star$] $>$24 Soldiers from bases around the world.
\item[$\star$] Comments: ``Dr.~Tschopp and Dr.~Hobbs were phenomenal. [...] I loved the course, and it was encouraging to know that we have 1600 researchers pioneering the way ahead for the armed forces. With the outlook, skills, and knowledge gained from the course I have a significantly better understanding of the capabilities and limitations of AI.''
\item[$\star$] ``Artificial Intelligence for Soldiers 2024,'' ARL-SR-0497 (112 pages), summarized the development and feedback from this inaugural course.
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Artificial Intelligence 101,'' Rock Island Arsenal, AMC Joint Munitions Command HQ, 30 SEP 2023 (8-h total).
\begin{list2}
\item[$\star$] $>$100 registered participants.
\item[$\star$] Post-course survey: ``Overall evaluation of course is excellent'' (4.91/5.0), ``Instructor is excellent'' (4.97/5.0), ``Highly recommend to others'' (4.97/5.0)
\item[$\star$] Comments: ``I really loved this course! I have already recommended it to just about everyone I have spoken to, haha!'', ``Great class. Mark is also a very good instructor.'', ``Mark did a great job!'', ``S-tier break screens, Mark''
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Fourth Be With You,'' Microsoft TEAMS, 4--5 MAY 2023 (15-h total).
\begin{list2}
\item[$\star$] $>$350 registered participants, 3000 person-hours of ML instruction, 2 guest speakers.
\item[$\star$] Post-course survey: ``Overall evaluation of course is excellent'' (4.91/5.0), ``Instructor is excellent'' (4.97/5.0), ``Highly recommend to others'' (4.97/5.0)
\item[$\star$] ``Dr.~Tschopp's course was one of the rare courses that teaches an incredibly complex subject effectively to a diverse audience from PhDs to old engineers like me 22 years out of college (25 out of linear algebra!).  Outstanding job!''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Dashboarding 101: Unlocking Your Data's Story with Excel Wizardry,'' Microsoft TEAMS, 15 DEC 2022 (2-h total).
\begin{list2}
\item[$\star$] 90+ attendees, ``THANK YOU SO MUCH!'', ``Great class!!!!'', etc.
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Artificial Intelligence 101,'' Continuing Education for Senior Leaders (CESL) Information Advantage, 31 OCT 2022 (3.5-h total).
\begin{list2}
\item[$\star$] Collaboration with Army TRADOC CAC Army Management Staff College in Fort Leavenworth.
\item[$\star$] ``And on behalf of the remaining MDO faculty here at AMSC, I would like to say thank you, thank you, thank you. I had mentioned your name when asked about who might be able to step in, and I can't tell you how relieved I was that you were doing it.''
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The End of the Fiscal Year Be With You,'' Microsoft TEAMS, 29--30 SEP 2022 \& 27--28 OCT 2022 (each session, 15-h total).
\begin{list2}
\item[$\star$] $>$350 registered participants, 85\% Army/DoD audience, 1600 person-hours of ML instruction, 3 guest speakers.
\item[$\star$] ``The course was well presented and engaging.  This was probably the most engaging course I've ever had, especially for such a complex and technical topic.  You well exceeded expectations coming in.  You should teach a course on how to build engaging courses, because a lot of people could use some help.''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Fourth Be With You,'' Microsoft TEAMS, 3--4 MAY 2022 (15-h total).
\begin{list2}
\item[$\star$] $>$250 registered participants, 85\% Army audience, 1600 person-hours of ML instruction, 3 guest speakers.
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Course Be With You,'' Microsoft TEAMS, 28--29 OCT 2021 (12-hour total).
\begin{list2}
\item[$\star$] $>$100 registered participants.
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: ML + Cyber,'' Army DEVCOM C5ISR, 3--5 AUG 2021 (20-hours total).
\begin{list2}
\item[$\star$] Taught cyber applications of machine learning algorithms with ARL Cyber scientist Dr.~Mike De Lucia.
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Fourth Be With You,'' Army TRADOC CAC Army Management Staff College, 27--29 JULY 2021 (8-hour total).
\begin{list2}
\item[$\star$] 15 faculty responsible for educating and developing Army Civilian Corps (including Army Senior Leaders) for leadership and management responsibilities.
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: May The Fourth Be With You,'' Microsoft TEAMS, 4 MAY 2021 (8-hours total).
\begin{list2}
\item[$\star$] 800 registered participants from around the world.
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: Bullets, Armor, Weapons, and a little Additive Manufacturing,'' University of Memphis, 11--12 MAR 2021 (8-hours total).
\begin{list2}
\item[$\star$] 90 registered participants, from over a dozen institutions around the country (majority from U Memphis, Mississippi State University, Ole Miss, industry).
\item[$\star$] Multiple segments added for additive manufacturing examples with machine learning, including ML--XLS tutorial session
\item[$\star$] ``It is an excellent course. Breaking complex forms into simple excel documents is brilliant. One can visualize and understand what is going on.''
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: Primer and Episode IV,'' Microsoft TEAMS, ARL Caf\'{e}, 5 MAR 2021 (2.5 hours).
\begin{list2}
\item[$\star$] 60+ ARL attendees (plus AFC, PEO). ``Course is excellent'' (4.9/5), ``Instuctor is excellent'' (5.0/5)
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: Primer, Episodes IV, V, VI, and ML for Excel,'' Spelman University, 19--20 JAN 2021 (6-hour course).
\begin{list2}
\item[$\star$] 28 attendees, mostly faculty from departments ranging from Computer Science to Physics to Economics.  This course was supporting an ARL cooperative agreement with Spelman University designed to develop an AI/ML-based curriculum.  
\item[$\star$] Invited back to kickoff summer faculty forum
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``ML by XLS: Machine Learning by Microsoft Excel,'' Microsoft TEAMS, ARL Caf\'{e}, 11 DEC 2020 (2 hours).
\begin{list2}
\item[$\star$] 34 ARL attendees. 
\item[$\star$] ``Great presentation!'', ``Thanks for the insights!'', ``Thanks Mark, very insightful''  
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: Episode V, VI,'' Microsoft TEAMS, ARL Caf\'{e}, 16 OCT 2020 (2 hours).
\begin{list2}
\item[$\star$] 79 ARL attendees. Over 30 views on Microsoft Stream. 
\item[$\star$] ``Bravo! Thanks again Mark!''
\end{list2}


\item
\textbf{Tschopp, M.A.}, ``Machine Learning for Everyone: Primer and Episode IV,'' Microsoft TEAMS, ARL Caf\'{e}, 2 OCT 2020 (2 hours).
\begin{list2}
\item[$\star$] 27 ARL attendees. Over 160 views on Microsoft Stream. 
\item[$\star$] ``I enjoyed it!'', ``I second that!'', ``This is awesome!! Thank you for putting this together!'', ``Thank you, great talk and really appreciate all the thought and work you put into this. I'd like to know how to make those star wars scrolling dialog'', ``Thanks Mark! Probably the best and most concise presentation of the topic I have seen to date. I really appreciate the extra work with the V50 data. I would love to comb through the xlsx's for kicks and giggles.''  
\end{list2}

\item
\textbf{Tschopp, M.A.}, ``Machine Learning 101: Pilot Seminar,'' Microsoft TEAMS, ARL--WMRD, AUG 2020 (1.5 hour).

\end{cvlist}
