\section{\sc University\\Courses\\Taught}
Mississippi State University \\
{\bf Advanced Mechanics of Materials} \\ 
{\it Textbook:} A.C. Ugural and S.K. Fenster, {Advanced Strength and Applied Elasticity} \\
{\it Instructor(s):} M.A. Tschopp (instructor of record) \\
{\em Engineering Mechanics 4213/6213} \hfill    {\bf Spring 2011} \\
Global Index: 4.5/5.0 (14 students)

\begin{list2}
\vspace*{.05in}
\item	Student Evaluations (14 students):
\vspace*{.05in}
	\begin{list2}
	\item Global Index: 4.5/5.0
	\item The instructor created high expectations for the class: 4.8/5.0
	\item The instructor was enthusiastic about the subject matter: 4.8/5.0
	\item Tests and/or assignments were graded within a reasonable period of time: 4.8/5.0
	\item The instructor was accessible outside of class time to respond to my questions or concerns: 4.7/5.0
	\item The tests reflected material presented in lecture and/or assigned reading: 4.5/5.0
	\item I learned a great deal in this class: 4.5/5.0
	\item I would recommend this instructor to other students if they wanted to learn this subject: 4.5/5.0	
	\end{list2}
	\item	Student feedback from class (via email):
\vspace*{.05in}
	\begin{list2}
	\item ``I had a great time in your class this semester. You are a wonderful teacher and I learned a great deal from you.''
	\item ``Your class was challenging and I enjoyed many parts of it.  It definitely stretched me.  Thanks for putting up with my `squeaky wheel,' you were very attentive to the issues of us distance students and I really appreciate that.''
	\item ``I really enjoyed the class and learned a lot, and from talking to everyone else I think they all feel the same way.''
	\item ``Thanks for a great semester.''
	\item ``Teach more classes!!!''
	\end{list2}
\end{list2}

Georgia Institute of Technology \\
{\bf Statistics \& Numerical Methods for Material Science and Engineering} \\ 
{\it Textbook:} Chapra and Canale, {Numerical Methods for Engineers} \\
{\it Instructor(s):} M.A. Tschopp, D.L. McDowell (instructor of record) \\
{\em Material Science \& Engineering 3803} \hfill    {\bf Fall 2005} \\
Global Index: 4.5/5.0 (16 students)

\begin{list2}
\vspace*{.05in}
\item This course was a new undergraduate course that introduced MSE students to computational numerical methods for solving mathematical problems.  This class was taken in conjunction with the ME 7757 -- Teaching Practicum, a class designed to introduce Ph.D. students to different career paths after their doctoral studies.
\item	Responsible for \textit{seven} 90-minute lectures throughout the semester.  This involved preparing Powerpoint slides, in-class examples, and notes for these classes.  Topics included: Roots of Polynomials, Gauss Elimination, LU decomposition and Matrix Inversion, Least-Squares Regression, Interpolation, Newton-Cotes Integration, and Boundary-Value and Eigenvalue Problems.
\item	Responsible for \textit{four} programming sessions that introduced students to the Visual Basic application within Excel and MATLAB as programming languages.  I prepared Powerpoint slides for all of these lectures. 
\item	Responsible for grading and preparing solutions for homework \#1 through \#4, as well as answering questions during office hours each week for students.  
\item	Student Evaluations (16 students):
	\begin{list2}
	\item Was approachable and willing to assist students: 4.94 out of 5
	\item Knowledgable about subject: 4.63 out of 5
	\item Encouraged students to consult with him: 4.63 out of 5
	\item Was prepared and organized: 4.63 out of 5
	\item Was dedicated to teaching: 4.63 out of 5
	\item Overall, has been an effective teacher: 4.50 out of 5
	\end{list2}
\end{list2}

