\section{\sc Mentoring / Advising}

\textit{Advisee positions and affiliations below reflect status as last verified (circa 2025).}

Formal Mentoring Programs
\begin{list2}
\vspace*{.05in}
\item
2020--Present, ARL Mentoring Program, \textbf{Five} ARL Civilians (formally).

\item
2020--Present, NDSEG Fellow Mentor Program, \textbf{Two} NDSEG Fellows at UT-Austin, UNC.

\item
2020--Present, ARL Mentor (informal), monthly/bimonthly meetings

\end{list2}

Post-Doctoral Fellows and Visiting Scientists

\begin{list2}
\vspace*{.05in}
\item
\href{https://www.linkedin.com/in/philip-goins-89982636}{Dr.~Philip Goins} (2016--2017, ARL) ``Mesoscale modeling of polycrystalline evolution during additive manufacturing,'' Staff Scientist, Army Research Laboratory.
\item
\href{https://www.researchgate.net/profile/Efrain_Hernandez-Rivera}{Dr.~Efrain Hernandez} (2015--2017, ARL) ``Hybrid statistical--deterministic models for microstructure evolution at the mesoscale,'' Staff Scientist, Army Research Laboratory.
\item
\href{https://www.researchgate.net/profile/Krista_Limmer}{Dr.~Krista Limmer} (2016, ARL) ``Multiscale modeling and simulation of corrosion in magnesium and magnesium alloys,'' Staff Scientist, Army Research Laboratory.
\item
\href{http://scholar.google.com/citations?user=Ueq2NM4AAAAJ&hl=en}{Dr.~Shawn Coleman} (2014--2016, ARL) ``Virtual diffraction methods in atomistic simulations,'' Regional Lead, Army Research Laboratory.
\item
Dr.~Andrew Oppedal (2012--2014, MSU) ``High temperature creep and failure of single crystal nickel-based superalloys (AFOSR),'' Research Faculty, Center for Advanced Vehicular Systems, Mississippi State University.
\item
\href{http://scholar.google.com/citations?user=f9_ceZEAAAAJ&hl=en}{Dr.~Ebrahim Asadi} (2011, MSU) ``Atomistic simulations of stacking fault energy interactions with point defects,'' Associate Professor, University of Memphis.
\item
\href{http://scholar.google.com/citations?user=b0N71IgAAAAJ&hl=en}{Dr.~Sasan Nouranian} (2011--2012, MSU) ``Forcefield development for saturated hydrocarbons and polyolefins using MEAM,'' Associate Professor, Ole Miss.
\item
Dr.~Xing Qiao (Sheldon) Deng (2011--2012, MSU) ``Out-of-position (OOP) air bag deployment and passenger impact,'' Associate Professor, Xihua University, Chengdu, China.
\item
\href{http://scholar.google.com/citations?user=lpxuxN8AAAAJ&hl=en}{Dr.~Marcos Lugo} (2010--2012, MSU) ``Damage and microstructure evolution in aluminum and magnesium,'' Associate Professor, Liberty University.
\item
Dr.~Delwar Hossain (2009--2010, MSU) ``Atomistic simulations of deformation mechanisms in thermoplastic polymers,'' Instructor and Lab Coordinator, Claflin University.
\end{list2}

Graduate students (Ph.D., M.S.)

\begin{list2}
\vspace*{.05in}
\item
Dr.~Nick Lauersdorf (2022--2024, UNC-Chapel Hill), NDSEG Fellow, Data Scientist, Advance Medical Designs.
\item
Mr.~Kevin Scanlan (2021--2023, UT-Austin), NDSEG Fellow, Graduate student, UT-Austin.
\item
{Dr.~Mojtaba Khanzadeh} (2015--2019, MSU) ``Advanced data analytic methodology for quality improvement in additive manufacturing,'' Applied Scientist, Amazon.
\item
\href{https://scholar.google.com/citations?hl=en&user=feOs0wcAAAAJ}{Mr.~Yub Raj Paudel} (2015--2018, MSU) ``On the localized effects of twinning, mechanisms driving twin segmentation of the parent grain, and building a strategy to incorporate them in full-field plasticity,'' Research Engineer II, Center for Advanced Vehicular Systems, Mississippi State University.
\item
Dr.~Daniel Foley (Summer 2015, ARL) ``Understanding Deformation Behavior of Nanocrystalline Metals Using Virtual Diffraction Characterization on Multi-million Atom Simulations,'' Engineer, Savannah River Nuclear Solutions.
\item
\href{http://scholar.google.com/citations?user=DMtfKn0AAAAJ&hl=en}{Dr.~Christopher Barrett} (2011--2014, MSU) ``Twin nucleation in single crystal Mg,'' Associate Professor, Mississippi State University.
\item
\href{https://www.researchgate.net/profile/Scott_Turnage}{Dr.~Scott Turnage} (2012--2014, ASU) ``Relationship between material uncertainty and high temperature creep of single crystal nickel-based superalloys (AFOSR),'' ARL Staff Scientist, Army Research Laboratory.
\item
Dr.~Xiumei (Emily) Zhang (2010--2011, MSU) ``Molecular deformation in glucose and polypropylene/carbohydrate interfaces.''
\item
\href{http://scholar.google.com/citations?user=MjAcNi8AAAAJ&hl=en}{Dr.~Mehul Bhatia} (2011--2015, MSU/ASU) ``Molecular dynamics simulations of void growth in single crystal Al and Al grain boundaries,'' Assistant Professor, Worcester Polytechnic Institute.
\item
\href{http://scholar.google.com/citations?user=l-oMnVsAAAAJ&hl=en}{Dr.~Ilaksh Adlakha} (2011--2015, MSU/ASU) ``Effect of hydrogen on the strength and embrittlement of materials in confined volumes,'' Associate Professor, IIT-Madras.
\item
\href{http://scholar.google.com/citations?user=-Wia-SkAAAAJ&hl=en}{Dr.~Mohsen Eshraghi} (2012) ``Effect of resistance spot welding parameters on weld pool properties in a DP600 dual-phase steel,''  Professor, California State University--Los Angeles.
\item
Mr.~Kris McKenzie (2012--2013, ARL) ``Mesoscale Modeling of Dislocation Interactions during Twinning in HCP Metals.'' 
\item
\href{https://scholar.google.com/citations?view_op=list_works&hl=en&hl=en&user=J1DJ_3YAAAAJ}{Dr.~Mansa Rajagopalan} (2014--2015, ASU) ``Influence of grain boundary structure on segregation and fracture,'' Manager, Engineering, Lam Research. 
\item
\href{http://scholar.google.com/citations?user=u0b0HCUAAAAJ&hl=en}{Dr.~Laalitha Liyanage} (2010--2012, MSU) ``Electronic and atomistic calculations of steel alloys using modified embedded atom method and density functional theory,'' Senior lecturer, University of Kelaniya, Sri Lanka.
\item
\href{http://scholar.google.com/citations?user=8YpvYScAAAAJ&hl=en}{Mr.~Suryatej Potula} (2010--2012, MSU) ``{Study of out-of-position (OOP) air bag deployment and passenger impact},'' Safety CAE Analyst, Optimal Computer Aided Engineering, Inc.

\end{list2}

Undergraduate students

\begin{list2}
\vspace*{.05in}
\item 
Ms.~Mya Powers-Nash (2021--2022, Chicago State University) ``Machine Learning and Energetic Materials: Using Machine Learning to characterize molecular structure for energetic materials,'' Ph.D. student, University of Chicago.
\item
Mr.~Phillip Spear (Summer 2012, MSU/Tuskegee) ``Dislocation nucleation from Cu-Ni-Nb multilayers,'' Project engineer, Pratt \& Whitney.
\item
Ms.~Tikelia Wright (Summer 2012, MSU/Tuskegee) ``Generation and Mechanics of Cu-Ni-Nb multilayers,'' Engineer Specialist, Honda Manufacturing.
\item
Mr.~Nathan R. Rhodes (2011, MSU) ``Grain boundary segregation for advanced materials design,'' Ph.D. student, University of Florida.
\item
Mr.~Mohit Shrivastava  (Summer 2011, MSU) ``Deformation in amorphous polyethylene using full-atom models,'' Data Center Engineer, Amazon.
\item
Mr.~Suman Kandel (2011, MSU) ``Exploring deformation behavior of mono- and polycrystalline nanowires,'' ME Contractor, Self-Employed.
\item
Mr.~Dmitry Zhuk (2011, MSU) ``Stress-state dependence of glassy polymers at the nanoscale,'' Lead Engineer, Moscow Engineering Physics Institute.
\item
\href{http://scholar.google.com/citations?user=DMtfKn0AAAAJ&hl=en}{Mr.~Christopher Barrett} (Summer 2010, MSU) ``Twin nucleation in single crystal Mg,'' Assistant Professor, Mississippi State University.
\item
Mr.~Chesley Rhodes (Summer 2010, MSU) ``Grain boundary structure and energy in HCP metals,'' Engineering Manager, Lockheed Martin.
\item
Mr.~Mohit Shrivastava  (Summer 2010, MSU) ``Deformation in amorphous polyethylene using full-atom models,'' Data Center Engineer, Amazon.
\item
Ms.~Mukti Patel  (Summer 2010, MSU) ``Molecular deformation in amorphous polypropylene,'' PhD, Associate Materials Engineer, Tesla.
\item
Mr.~Shashwat Namdeo (Summer 2010, MSU) ``Influence of impurities on dislocation/twin nucleation in Mg,'' Application Developer, Fallon Health.
\end{list2}

High school students
\begin{list2}
\vspace*{.05in}
\item
Ms.~Joanna Sun, ``Segregation of Cr to Fe grain boundaries,'' PNNL summer intern (2012--2013).

\end{list2}

Committee member (M.S., Ph.D.)
\begin{list2}
\vspace*{.05in}
\item
\href{https://www.researchgate.net/profile/Yubraj_Paudel}{Mr.~Yubraj Paudel}, ``On the localized effects of twinning, mechanisms driving twin segmentation of the parent grain, and building a strategy to incorporate them in full-field plasticity,'' Ph.D. ME student, Mississippi State University (October 2018).
\item
\href{http://scholar.google.com/citations?user=DMtfKn0AAAAJ&hl=en}{Mr.~Christopher Barrett}, ``\href{http://sun.library.msstate.edu/ETD-db/theses/available/etd-03212014-133222/}{Relations and interactions between twinning and grain boundaries in hexagonal close-packed structures},'' Ph.D. ME student, Mississippi State University (March 2014).
\item
\href{http://scholar.google.com/citations?user=8YpvYScAAAAJ&hl=en}{Mr.~Suryatej Potula}, ``\href{http://sun.library.msstate.edu/ETD-db/theses/available/etd-12092011-130158/}{Study of out-of-position (OOP) air bag deployment and passenger impact},'' M.S. ME student, Mississippi State University (May 2012).
\end{list2}

Career Development, Mentoring, and STEM Outreach Activities
\begin{itemize}
\item Tschopp, M.A., ``STEM Career Day,'' Neuqua Valley High School, Naperville, IL, 17 NOV 2023.
\item Tschopp, M.A., ``Research and Technology for Operating Environments of the Future, i.e., Cool Stuff that We are Working On"," Peoria Public School District \& First Robotics Competition, Peoria, IL, 6 SEP 2019.
\begin{list2}
\item Peoria Public Schools, Manual Academy Robo Rams' FIRST Tech Challenge Kickoff, 6 SEP 2019.
\item 425 9th--12th grade students from Peoria Public Schools
\item I gave the kickoff talk about the value of STEM within the Army and the mission of the Army Research Laboratory.
\end{list2}

\item \href{https://www.army.mil/article/212535/army_lab_recognizes_scientific_contributions_of_postdocs_at_symposium}{ARL 3rd annual Postdoc Research Symposium}, Career Development panel (w/ David Stepp, Betsy Rice)

\item Tschopp, M.A., ``Materials Science and Engineering,'' STEM Outreach at local elementary school (Homestead Wakefield Elementary School), 7 APR 2017.
\begin{list2}
\item 50 fourth graders, 2 teachers (7 APR 2017) 
\item ARL Press Release, ``\href{https://www.army.mil/article/186569/army_materials_researcher_shares_passion_for_science_with_kids}{Army Researcher Makes Science Real for Elementary Students}'' 
\item Asked to return for remaining classes.
\end{list2}
\item Tschopp, M.A., ``Materials Science and Engineering,'' STEM Outreach at local elementary school (Homestead Wakefield Elementary School), 2 JUN 2017.
\begin{list2}
\item 100 fourth grade students, 4 teachers
\end{list2}


\item ``Meet-A-Mentor,'' Professional Development \& Special Lectures, TMS 2016, 02/15/2016. \textit{This event matches mentors and mentees for scheduled meetings in an informal atmosphere.}
\item ``Student Career Forum'' Invited Panel Member, TMS Young Professional Committee, TMS 2016, 02/14/2016.  \textit{Organized by the TMS Young Professional Committee, this session will feature speakers from various stages of their careers and diverse materials science backgrounds to discuss how to navigate a successful career path in the fields of minerals, metals, and materials.}
\item “I got my degree. What now?" Invited Panel member at MS\&T 2015
\item ``Undergraduate writing/presenting workshop,'' helped with workshop at MS\&T Conference 2015, 10/05/2015.
\item Symposium Organizer for Early Career Professionals
\begin{list2}
\item	Symposium organizer for MS\&T 2012, ``Perspectives for the Emerging Professionals''
\begin{list2}
\item
\textbf{Tschopp, M.A.}, ``\href{http://amp.digitaledition.asminternational.org/i/80917/60}{MS\&T 2012 Symposium for Emerging Professionals: Early Strategies for Career Development},'' ASM International Advanced Materials \& Processes, Fall 2012.
\end{list2}

\item	Symposium organizer for MS\&T 2013, ``Perspectives for the Emerging Professionals''
\begin{list2}
\item
\textbf{Tschopp, M.A.}, ``\href{http://amp.digitaledition.asminternational.org/i/147077/59}{Career Opportunities and Experiences in Materials Science and Engineering},'' ASM International Advanced Materials \& Processes, August 2013.
\item ``Thank you Mark for your outstanding organization. The symposium was well received, and I heard many accolades and encomiums for you and your team! ASM thrives on your enthusiasm! Warmest regards, wishing you continued successes!'', Dr.~Ravi Ravindran, ASM President
\end{list2}
\item	Symposium organizer for MS\&T 2014, ``Perspectives for the Emerging Professionals''
\begin{list2}
\item  2 sessions, 2 keynote speakers, 9 invited speakers
\item  Gave Introductory Presentation
\item  Chaired 2 sessions
\end{list2}
\end{list2}

\item Industry Mentor at ``Lunch with Industry'' Student Mentoring Event at MS\&T 2013.
\item Course instructor for ``Materials Engineering'' for 8-11$^{th}$ grade students, Wright STEPP program at Wright State University, 2009. 
\item Course instructor for ``Materials Engineering for Automobiles and Monster Trucks'' for 1$^{st}$-3$^{rd}$ grad students, Saginaw Elementary Schools, 2001.
\end{itemize}





