\section{\sc Funded Research Programs}

% The public list shows funded work. The comment layer is where you keep the full
% picture -- submitted vs. funded, and the proposals that didn't land (with why).
% None of it renders. Fictional examples:
%   @proposal sponsor=ARO   type=single-PI submitted=2021-02 amt=360K/3yr status=funded
%   @proposal sponsor=DARPA type=YFA       submitted=2020-09 amt=500K/2yr status=declined note="scope too broad"
%   @proposal sponsor=NSF   type=CAREER    submitted=2019-07 amt=500K/5yr status=declined note="resubmit w/ prelim data"
\begin{list2}
\item ``An ICME-based Approach for Laser-Based Additive Manufacturing of Novel Metal Powder Feedstocks: Tailorable Local Material Properties by Design and on Demand,'' co-PI, ARL 6.2 (2016).
\item ``Atomistic Understanding of the Role of Grain Boundary Structure in Lightweight Armor Systems,'' Mentor/PI, 2016 DoD HPCMP Internship Program, ARL (2016).
\item ``Mesoscale Modeling of Polycrystalline Microstructure Evolution under Magnetic Fields,'' Co-PI and Mentor, ARL (2016).
\item ``Transitioning Material Systems from Laboratory to Fabrication (CA),'' ARL TPOC, ARL (2015).
\item ``Interfacial Engineering of Aluminum-Based Alloys for Ballistic Protection,'' PI, ARL (2015).
\item ``Understanding Deformation Behavior of Nanocrystalline Metals Using Virtual Diffraction Characterization on Multi-million Atom Simulations,'' Mentor/PI, 2015 DoD HPCMP Internship Program, ARL (2015).
\item ``Realistic Implementation of Energy Coupled to Matter,'' co-PI, ARL (2015).
\item ``Virtual Diffraction: Connecting Atomistic Simulations with Experiments to Understand Nanocrystalline Deformation Behavior,'' co-PI and Mentor, ARL (2015).
\item ``Exploiting Oxide Dispersion Strengthening in Ferritic Alloys for Lethality Applications,'' co-PI, ARL 6.2 (2015).
\item ``Atomistic and Mesoscale Modeling for Grain Boundary Engineering: Computationally-Driven Approach for Exploiting Interfacial Structure-Property Relationships,'' PI, ARL 6.1 (2014).
\item ``Towards Predictive Models of Nanocrystalline Binary Metal Alloys: Role of Solutes and Interfaces on Segregation and Mechanics in Al-based Nanocrystalline Systems,'' co-PI, ARL (2013).
\item ``Low Cost Structural Thermoelectrics: New Possibilities for Turning Waste into Energy,'' PI, ARL (2013).
\item ``Hierarchically-driven approach for quantifying materials uncertainty in creep deformation and failure of aerospace materials,'' PI (MSU), AFOSR (2012).
\begin{list2}
\item Submitted as AFOSR YIP.  Awarded as sole PI grant.
\end{list2}
\item ``The Effects of the Uncertainty of Thermodynamic and Kinetic Properties on Nucleation and Evolution Kinetics of Cr-Rich Phase in Fe-Cr Alloys,'' PI (MSU), DOE NEAMS (2011).
\end{list2}
