\section{\sc Service}

\textit{Army Research Laboratory}
\begin{list2}
\item ARL Fellows 
\begin{list2}
\item Co-Chair (2021-2022), Chair (2022-2023)
\end{list2}

\item Employee Advisory Council (EAC) -- Workforce Enrichment, Recruitment, Retention (WERR)
\begin{list2}
\item Chair, EAC-WERR (2022-2023), elected as inaugural chair
\item Chair/Member, Governance subcommittee
\end{list2}

\item Employee Advisory Council (EAC) -- Diversity, Equity, Inclusion, and Accessibility (DEIA)
\begin{list2}
\item Governance subcommittee
\item Data Analytics \& Metrics subcommittee
\end{list2}

\end{list2}

\textit{Journal Reviewer / Editorial Board}

\begin{list2}
\item Selected to the Editorial Board of Metallurgical Transactions A, 02/11/2016 (Key Reader).

\item Modelling and Simulation in Materials Science and Engineering, Physical Review B, Physical Review Letters, Acta Materialia, Computational Materials Science, International Journal of Plasticity, Computers, Materials, and Continua, Philosophical Magazine, International Journal of Fatigue, Metallurgical and Materials Transactions, Applied Surface Science, Surface Science, Journal of Materials Science, Nanotechnology, Journal of Physics: Condensed Matter, Journal of Physics D: Applied Physics, Materials Research Letters, Nature Scientific Reports, etc.

\item Metallurgical and Materials Transactions A: Excellent Reviewer (2012, 2015)

\item Guest Editor, JOM, ``Algorithm Development in Computational Materials,'' with Zimmerman, J., Sabau, A., Zaeem, M.A., Spearot, D.

\end{list2}

\textit{Proposal Panels and Reviews}

Reviewer of various NSF, DOE, OSD, AFOSR, ARO, and ARL program and proposals, including international proposals in Europe.

Invited member for AIR FORCE S\&T 2030 INITIATIVE (\href{https://apps.dtic.mil/sti/pdfs/AD1062947.pdf}{Report})

\textit{ARL Workshops / Engagement}
\begin{list2}
\item ``Data-Driven Design of Hierarchical Materials,'' co-organized with Evan Runnerstrom, Shawn Coleman, and U Chicago PIs, moderated the session on hard materials, 31 AUG 2020--1 SEP 2020.
\item Contributed invited article for ARL Publication ``Research@ARL: Materials Modeling at Multiple Scales'' (editors: J. Andzelm, G. Gazonas, J. McCauley)
\item Chair, breakout session on Computational Modeling for Additive Manufacturing in DOD at AHPCRC's ``Computational Methods and Tools for Additive Manufacturing for Defense Applications,'' Adelphi, MD (12/16/15).
\end{list2}

\textit{Professional Society Leadership}
\begin{list2}
\item Member, American Society of Mechanical Engineers (ASME), Fellow.
\item Member, American Society of Metals (ASM), Fellow.
\item Member, American Association for the Advancement of Science (AAAS).
\item Member, Minerals, Metals, and Materials Society (TMS).
\item ``\href{http://mio.asminternational.org/amp/201801/40/}{Profile of a Volunteer: Mark Tschopp},'' AM\&P Magazine, p.~40.  

\item Member, ASM Award Selection Committee, 1/1/2017--1/1/2020.
\item Chair, ASM Silver Medal Selection Committee, 1/1/2017--1/1/2018.
\item Member, ASM Emerging Professionals Committee (EPC), 9/1/2011--8/31/2014.
\item Member, ASM Silver Medal Selection Committee, 9/1/2014--8/31/2016.
\item Member, ASM Materials Property Database Committee, 9/1/2015--8/31/2018.

\item Chair, ASM EPC Programming SubCommittee, 9/1/2011--8/31/2014.
\begin{list2}
\item	Symposium organizer for MS\&T 2012, ``Perspectives for the Emerging Professionals''
\item	Symposium organizer for MS\&T 2013, ``Perspectives for the Emerging Professionals''
\begin{list2}
\item ``Thank you Mark for your outstanding organization. The symposium was well received, and I heard many accolades and encomiums for you and your team! ASM thrives on your enthusiasm! Warmest regards, wishing you continued successes!'', Dr.~Ravi Ravindran, ASM President
\end{list2}
\item	Symposium organizer for MS\&T 2014, ``Perspectives for the Emerging Professionals''
\begin{list2}
\item  2 sessions, 2 keynote speakers, 9 invited speakers
\item  Gave Introductory Comments
\end{list2}
\item Chaired all sessions (6 total)
\end{list2}

\item Member, TMS Integrated Computational Materials Engineering Committee, 2010--Present.
\begin{list2}
\item	Symposium co-organizer for TMS 2018, Francesca Tavazza; Mark Tschopp; Richard Hennig; Avinash Dongare; Shawn Coleman; Niaz Abdolrahim; Joseph Bishop; Fadi Abdeljawad; Li Ma, ``Computational Method and Experimental Approaches for Model Development and Validation, Uncertainty Quantification, and Stochastic Predictions''
\item Lead organizer of multiple sessions on Interatomic Potential Development

\item Chair, Programming Subcommittee (2014--2016)
\begin{list2}
\item Co-organizer, Data and Tools for Materials Discovery and Design, MS\&T 2017.
\item	Symposium lead organizer for TMS 2016, Mark Tschopp, Carelyn Campbell, Francesca Tavazza, Sheng Yen Li, Dongwon Shin, Jiadong Gong, Junsheng Wang, ``ICME Infrastructure Development for Accelerated Materials Design: Data Repositories, Informatics, and Computational Tools''
\item	Symposium co-organizer for TMS 2016, Francesca Tavazza, Richard Hennig, Mark Tschopp, Li Ma, ``Computational methods for uncertainty quantification, model validation, and stochastic predictions''
\item	Symposium co-organizer for TMS 2016, Michael Tonks, Julie Tucker, Mark Tschopp, Richard Williamson, ``Computational Materials Engineering for Nuclear Reactor Applications''
\item Responsible for ICME programming within TMS for 4 year span
\end{list2}
\item Secretary (2010--2012)
\item Cyberinfrastructure Subcommittee, 2010--2013
\end{list2}

\item Member, TMS High Temperature Alloys Committee, 2012--Present.
\begin{list2}
\item	Symposium organizer for TMS 2015, ``Multi-scale Microstructure, Mechanics \& Prognosis of High Temperature Alloys''
\begin{list2}
\item  7 sessions, 2 keynote speakers, 20 invited speakers, 60 talks total
\item  Gave Introductory and Closing Comments
\item  Chaired 6 sessions
\item  Editor for Special Issue in Metallurgical Transactions for Best Papers
\end{list2}
\end{list2}

\item Member, TMS Computational Materials Science Committee, 2013--Present.
\begin{list2}
\item	Symposium co-organizer for TMS 2014, ``Algorithm Development in Computational Materials Science and Engineering''
\end{list2}

\item Member, TMS/ASM Mechanical Behavior Committee, 2013--Present.

\item Member, ASME Applied Mechanics Division and Materials Division Joint Committee on Constitutive Equations, 2013--Present.
\begin{list2}
\item Secretary (2013--2015)
\item	Symposium co-organizer for ASME 2013, ``Multiscale Modeling of Fatigue Damage and Failure Mechanics''
\item Symposium co-organizer for ASME IMECE 2016, ``Damage and Failure Mechanics: Multiscale Approach, Experimental Characterization, and Modeling'' (all invited speaker symposium).
\item Symposium co-organizer for ASME IMECE 2017, ``Damage and Failure Mechanics: Multiscale Approach, Experimental Characterization, and Modeling''
\end{list2}
\item Member, ASME Applied Mechanics Division Fracture and Failure Mechanics Committee, 2013--Present.

\item Student assistant (A/V help, tour guide for GT campus), International Conference on Fatigue, 2006.
\item Session chair (not mentioned above)
\begin{list2}
\item Multiple sessions on adhoc basis: International Conference on Fracture, ASME IMECE, TMS, MS\&T.
\item `Atomistic Fracture and Deformation' symposium, International Conference on Fracture, 2009.
\item `Novel Approaches in Heterogeneous Materials Analysis and Characterization,' ASME IMECE, 2009.
\item `Multi Scale Modeling of Microstructure Deformation in Material Processing,' MS\&T 2011.
\item `Integrated Computational Modeling of Nuclear Materials: Modeling and Simulation of Material Phenomena', TMS 2013.
\item `Deformation and Transitions at Grain Boundaries' symposium,' MS\&T 2015.
\item `Data and Tools for Materials Discovery and Design symposium,' MS\&T 2015.
\item `Fracture and environmental defects symposium (12-32-1),' ASME IMECE 2015.
\item `Computational Materials Engineering for Nuclear Reactor Applications,' TMS 2016.
\item `Computational methods for uncertainty quantification, model validation, and stochastic predictions,' TMS 2016.
\item `Damage and Failure Mechanics: Multiscale Approach, Experimental Characterization, and Modeling,' ASME IMECE 2016.
\item `Damage and Failure Mechanics: Multiscale Approach, Experimental Characterization, and Modeling,' ASME IMECE 2017.
\end{list2}

\end{list2}

